### 2016-08-14 skimage_tomo.tex
Initial commit of latex file

%% BioMed_Central_Tex_Template_v1.06
%%                                      %
%  bmc_article.tex            ver: 1.06 %
%                                       %

%%IMPORTANT: do not delete the first line of this template
%%It must be present to enable the BMC Submission system to
%%recognise this template!!

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                     %%
%%  LaTeX template for BioMed Central  %%
%%     journal article submissions     %%
%%                                     %%
%%          <8 June 2012>              %%
%%                                     %%
%%                                     %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% For instructions on how to fill out this Tex template           %%
%% document please refer to Readme.html and the instructions for   %%
%% authors page on the biomed central website                      %%
%% http://www.biomedcentral.com/info/authors/                      %%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%% BioMed Central currently use the MikTex distribution of         %%
%% TeX for Windows) of TeX and LaTeX.  This is available from      %%
%% http://www.miktex.org                                           %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%% additional documentclass options:
%  [doublespacing]
%  [linenumbers]   - put the line numbers on margins

%%% loading packages, author definitions

\documentclass[twocolumn]{bmcart}% uncomment this for twocolumn layout and comment line below
%\documentclass{bmcart}

%%% Load packages
\usepackage{amsthm,amsmath}
%\RequirePackage{natbib}
\RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
\RequirePackage{hyperref}
\usepackage[utf8]{inputenc} %unicode support
%\usepackage[applemac]{inputenc} %applemac support if unicode package fails
%\usepackage[latin1]{inputenc} %UNIX support if unicode package fails
\usepackage{graphicx}
\usepackage{listings}
\usepackage{color}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                             %%
%%  If you wish to display your graphics for   %%
%%  your own use using includegraphic or       %%
%%  includegraphics, then comment out the      %%
%%  following two lines of code.               %%
%%  NB: These line *must* be included when     %%
%%  submitting to BMC.                         %%
%%  All figure files must be submitted as      %%
%%  separate graphics through the BMC          %%
%%  submission process, not included in the    %%
%%  submitted article.                         %%
%%                                             %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\includegraphic{}
%\def\includegraphics{}

\definecolor{listinggray}{gray}{0.1}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
	backgroundcolor=\color{lbcolor},
	tabsize=4,
	rulecolor=,
	language=Python,
        basicstyle=\scriptsize,
        %upquote=true,
        aboveskip={1.5\baselineskip},
        columns=fixed,
        showstringspaces=false,
        extendedchars=true,
        breaklines=true,
        prebreak = \raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
        frame=single,
        %showtabs=false,
        %showspaces=false,
        %showstringspaces=false,
        identifierstyle=\ttfamily,
        keywordstyle=\color[rgb]{0,0,1},
        commentstyle=\color[rgb]{0.133,0.545,0.133},
        stringstyle=\color[rgb]{0.627,0.126,0.941},
}

%%% Put your definitions there:
\startlocaldefs
\endlocaldefs

%%% Begin ...
\begin{document}

%%% Start of article front matter
\begin{frontmatter}

\begin{fmbox}
\dochead{Research}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the title of your article here     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{scikit-image, a Python library for 2D and 3D image
processing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors here                   %%
%%                                          %%
%% Specify information, if available,       %%
%% in the form:                             %%
%%   <key>={<id1>,<id2>}                    %%
%%   <key>=                                 %%
%% Comment or delete the keys which are     %%
%% not used. Repeat \author command as much %%
%% as required.                             %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\author[
   addressref={aff1},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   %noteref={n1},                        % id's of article notes, if any
   email={emmanuelle.gouillart@saint-gobain.com}   % email address
]{\fnm{Emmanuelle} \snm{Gouillart}}
\author[
   addressref={aff2},
   %email={}
]{\fnm{Juan} \snm{Nunez-Iglesias}}
\author[
   addressref={aff3},
   email={stefanv@berkeley.edu}
]{\fnm{Stéfan} \snm{Van der Walt}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter the authors' addresses here        %%
%%                                          %%
%% Repeat \address commands as much as      %%
%% required.                                %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\address[id=aff1]{%                           % unique id
  \orgname{Surface du Verre et Interfaces, UMR 125 CNRS/Saint-Gobain}, % university, etc                     %
  \postcode{93303}                                % post or zip code
  \city{Aubervilliers},                              % city
  \cny{France}                                    % country
}
\address[id=aff2]{%
  \orgname{Life Sciences Computation Centre, University of Melbourne},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Melbourne},
  \cny{Australia}
}
\address[id=aff3]{%
  \orgname{Division of Applied Mathematics, Stellenbosch University},
  %\street{D\"{u}sternbrooker Weg 20},
  %\postcode{24105}
  \city{Stellenbosch},
  \cny{South Africa}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Enter short notes here                   %%
%%                                          %%
%% Short notes will be after addresses      %%
%% on first page.                           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{artnotes}
%\note{Sample of title note}     % note to the article
%\note[id=n1]{Equal contributor} % note, connected to author
%\end{artnotes}

\end{fmbox}% comment this for two column layout

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% Please refer to the Instructions for     %%
%% authors on http://www.biomedcentral.com  %%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{abstractbox}

\begin{abstract} % abstract
\parttitle{First part title} %if any
Text for this section.

\parttitle{Second part title} %if any
Text for this section.
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The keywords begin here                  %%
%%                                          %%
%% Put each keyword in separate \kwd{}.     %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{keyword}
\kwd{scikit-image}
\kwd{Python}
\kwd{image processing library}
\kwd{3-D image}
\end{keyword}

% MSC classifications codes, if any
%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

\end{abstractbox}
%
%\end{fmbox}% uncomment this for twcolumn layout

\end{frontmatter}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Main Body begins here                %%
%%                                          %%
%% Please refer to the instructions for     %%
%% authors on:                              %%
%% http://www.biomedcentral.com/info/authors%%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%% See the Results and Discussion section   %%
%% for details on how to create sub-sections%%
%%                                          %%
%% use \cite{...} to cite references        %%
%%  \cite{koon} and                         %%
%%  \cite{oreg,khar,zvai,xjon,schn,pond}    %%
%%  \nocite{smith,marg,hunn,advi,koha,mouse}%%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%% start of article main body
% <put your article body there>

%%%%%%%%%%%%%%%%
%% Background %%
%%
\section*{Introduction}

The acquisition time of synchrotron tomography images has decreased
dramatically over the last decade, from hours to
seconds~\cite{Maire2014}. New modalities such as single-bunch
imaging~\cite{Rack2014} provide a time resolution down to the nanosecond
for radiography. However, the time subsequently spent in processing the
images has not decreased as much, so that the outcome of a successful
synchrotron imaging campaign often takes weeks or even months to be
transformed into scientific results.

Transforming billions of pixels and voxels to a few meaningful figures
represents a tremendous data reduction. Often, the sequence of operations
needed to produce these data is not known beforehand, or might be altered
due to artifacts~\cite{Marone2010}, or to an unforeseen evolution of
the sample. Image processing necessarily involves trial and error phases
to choose the processing workflow. Therefore, image processing tools need
to offer at the same time enough flexibility of use, a variety of
algorithms, and efficient implementations to allow for fast iterations
while adjusting the workflow.

Several software applications and libraries are available to synchrotron
users to process their images. ImageJ~\cite{Abramoff2004, Schneider2012}
and its distribution Fiji~\cite{Schindelin2012} is a popular tool for 2-D
and 3-D images, thanks to its intuitive menus and graphical tools, and
the wealth of plugins contributed by a vivid
community~\cite{Schindelin2015}. For 3-D images, commercial tools such as
Avizo 3D software (TM) are appreciated for an intuitive graphical
pipeline and advanced 3D visualization. Alternatively, the use of a
programming language gives finer control and more possibilities, provided
classical processing algorithms can be called from libraries -- hence
limiting the programming task and the risk of bugs. Matlab (TM) and its image
processing toolbox are popular in the academic community of computer
vision and image processing. The Python language is widely used in the
scientific world and in synchrotron facilitiies. As a general-purpose
language, Python is used in synchrotrons for controlling device
servers~\cite{pytango}, reconstructing tomography volumes from
radiographies~\cite{Gursoy2014, Mirone2014}, and various data processing
packages for macromolecular cristallography~\cite{Adams2010} or
fluorescence analysis~\cite{pymca}.

\texttt{scikit-image}~\cite{Vanderwalt2014} is a general-purpose image
processing library for the Python language, and a component of the ecosystem of
Python scientific modules commonly known as Scientific
Python~\cite{Oliphant2007}. Like the rest of the ecosystem,
\texttt{scikit-image} is released under a permissive open-source license and is
available free of charge. \texttt{scikit-image} is compatible with both 2-D and
3-D images, so that it can be used for a large number of imaging modalities,
such as microscopy, radiography or tomography. In this article, we explain how
\texttt{scikit-image} can be used for processing data acquired in synchrotron
imaging experiments, with a strong focus on microtomography 3-D images. This
article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
for X-ray imaging, but rather to explain the rationale behind the package, and
what can be done with \texttt{scikit-image}.

\section*{Overview and first steps}

In this section, we provide a short overview of the typical use patterns of
\texttt{scikit-image}, illutrated by short snippets of code. Indeed, since
Python is a programming language, the user interacts with data objects and
images through code, which is either typed and executed in an interactive
interpreter, or written in text files (scripts) that are executed.

Image are manipulated as numerical arrays of uniform
data type, a format that guarantees a fast access to the computer memory. The
n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
\texttt{NumPy} module~\cite{Vanderwalt2011}.

In image processing, one of the first tasks is therefore to generate
\texttt{NumPy} arrays, which is often done by reading data from files. Let us
read one 2-D image from a file and display it with the following lines of code:

\lstinputlisting[language=Python]{io.py}

\texttt{skimage} is the name under which \texttt{scikit-image} is imported in
Python code. Note that functions (such as \texttt{imread} to read an image
file, or \texttt{imshow} to display an image) are found in submodules of
\texttt{skimage}, such as \texttt{io}.

A stack of 2-D images, such as tomography slices generated by a reconstruction algorithm, can be opened as an image collection or a 3-D array:
\lstinputlisting[language=Python]{io_coll.py}
Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are opened using modules such as \texttt{h5py} or \texttt{pytables}.

\begin{figure*}
    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
 The gallery of examples consists of an array of thumbnails (left part),
 which link to example webpages, each centerered on a specific image
 processing task. Each webpage includes Python code generating a figure,
 the figure itself, as well as a short tutorial explaining the image
 processing operations and the code. \label{fig:ecosystem}}
\end{figure*}

\section*{The Python ecosystem}

The benefits of \texttt{scikit-image} for image processing come not only
from the features of the package alone, but also from the rich
environment of Scientific Python~\cite{Oliphant2007, Perez2011}.
Fig.~\ref{fig:ecosystem} illustrates how several components of this
ecosystem are used for a typical image processing workflow.

\paragraph{Interpreter and development environment.}

While several interpreters are available to execute interactively Python
instructions and scripts, the most popular one in the scientific world is
the IPython interpreter~\cite{Perez2007, Rossant2015}. IPython is an
advanced interpreter, which integrates for example a debugger,
introspection and profiling methods, and online help. Several IDEs
(Integrated Development Environment) integrate the IPython interpreter,
together with other components such as a text editor. For example, Spyder 
is a popular IDE (see Fig.~\ref{fig:spyder}).

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
  should go here. \label{fig:spyder}}
\end{figure*}

The Jupyter notebook~\cite{Kluyver2016} is a web application which has
grown from the IPython project, although the two projects have now
diverged. Jupyter notebooks provide an interactive development
environment within an Internet browser, where live code can be enriched
by explanatory text, equations and visualizations (figure or not??).

\paragraph{NumPy arrays}

- advanced operations in a compact form, at minimal memory consumption

- slicing to reduce memory cost

- nD : 2D, 3D, ...

\paragraph{Visualization libraries}

\paragraph{Advanced toolkits for signal processing and data science}

\texttt{scikit-image} is only one Python module that can be used for data
processing, among many others. A very popular module is
\texttt{scikit-learn}~\cite{Pedregosa2011}, a Python module for machine
learning using \texttt{NumPy} arrays. If local features of an image
(such as local statistics of gray levels, or geometric points of
interest), or features of segmented objects (e.g. geometrical and
intensity characteristics of segmented particles) are extracted with
functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}, it
is then possible to use a \emph{classification} algorithm of
\texttt{scikit-learn}, either for labeling pixels (a segmentation task)
or to classify whole images or objects that have already been segmented.
The interoperability between these packages is ensured by the common use
of \texttt{NumPy} arrays, so that the tasks described above are
implemented with a few lines of code.

The modularity of the Scientific Python ecosystem may look
confusing at first sight. Nevertheless, core modules of this ecosystem
are almost perfectly compatible, thanks to the shared use of NumPy arrays
and common development practices, although they are developed in parallel
by different teams.

\section*{Image processing capabilities}

\begin{figure}
    \centerline{\includegraphics[width=0.99\columnwidth]{mayavi_porous}}
\caption{\csentence{Sample figure title.}
      A short description of the figure content
      should go here.}
\end{figure}

\paragraph{Performance}

\section*{Documentation and getting help}

The success of a software package aimed at end-users is strongly
correlated to the quality of its documentation (find citation).
\texttt{scikit-image} users have access to different kinds of
documentation. Functions of the API (define API here or above) are all
documented using the same standard~\cite{Pawlik2015} as other major
Scientific Python packages. The standard include a description of all
input and output variables and their data type, together with
explainations on what the function does and how to use it. Functions
documentation is accessed either online, or within the development
environment (IPython, Spyder, Jupyter Notebook...).

\begin{figure*}
    \centerline{\includegraphics[width=0.99\textwidth]{figure_gallery}}
\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
 The gallery of examples consists of an array of thumbnails (left part), which link to example webpages, each centerered on a specific image processing task. Each webpage includes Python code generating a figure, the figure itself, as well as a short tutorial explaining the image processing operations and the code. \label{fig:gallery}}
\end{figure*}

In addition, a popular documentation tool is the graphical gallery of
examples (url), a part of which is displayed in Fig.~\ref{fig:gallery}.
The principle of the gallery is to accelerate the learning curve of image
processing, by displaying graphical examples of image processing
operations. Such examples are organized as an array of thumbnails with a
short title (see Fig.~\ref{fig:gallery} left). Thumbnails are links to
the webpage of the corresponding example, which features a mini-tutorial
on the image processing method, the code needed to run the example and
the figure generated by the example. Since the graphical gallery is an
efficient way to inform users about the features of
\texttt{scikit-image}, every new feature integrated in the package must
include an example for the gallery.

Longer tutorials and a more narrative documentation is available as well
in the User Guide of \texttt{scikit-image}. The User Guide explains in
particular...

Finally, tutorials on \texttt{scikit-image} are available in various places,
either as YouTube videos, or in the SciPy Lecture Notes~\cite{scipylecturenotes}, a comprehensive online book of Scientific Python tutorials.

\section*{Development and use of scikit-image}

\paragraph{Who uses scikit-image.}

Estimating the number of active users of an open-source package is a
difficult task. Statistics of downloads, for example, largely
overestimate the number of active users, all the more if the package is
bundled with others in a software distribution, like Anaconda or Canopy.
A view closer to reality can be obtained by analyzing the statistics of
visits of the online help, available on the project website.  As of the
first half of 2016, 20000 unique visitors per month visit the website of
scikit-image \url{http://scikit-image.org/}. These users come from 80
countries, located almost equally in Europe, America and Asia (Oceania
and Africa representing a much smaller fraction of visitors).

\paragraph{Development process.}

\texttt{scikit-image} is developed by a diverse team of volunteers, with
more than 170 developers that have contributed to the package. The
development process takes place on the GitHub platform
\url{https://github.com/scikit-image/scikit-image}, where users and
developers propose and discuss new contributions, or report bugs or ideas
for improvements.
A release cycle of one or two releases every year
ensures that new features are proprosed to users on a regular basis.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Backmatter begins here                   %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{backmatter}

\section*{Competing interests}
  The authors declare that they have no competing interests.

\section*{Acknowledgements}

The authors gratefully acknowledge the work of the contributors of
  \texttt{scikit-image}. E. Gouillart acknowledges the support of ANR
  project EDDAM ANR-11-BS09-027.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                  The Bibliography                       %%
%%                                                         %%
%%  Bmc_mathpys.bst  will be used to                       %%
%%  create a .BBL file for submission.                     %%
%%  After submission of the .TEX file,                     %%
%%  you will be prompted to submit your .BBL file.         %%
%%                                                         %%
%%                                                         %%
%%  Note that the displayed Bibliography will not          %%
%%  necessarily be rendered by Latex exactly as specified  %%
%%  in the online Instructions for Authors.                %%
%%                                                         %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% if your bibliography is in bibtex format, use those commands:
\bibliographystyle{bmc-mathphys} % Style BST file (bmc-mathphys, vancouver, spbasic).
\bibliography{refs}      % Bibliography file (usually '*.bib' )
% for author-year bibliography (bmc-mathphys or spbasic)
% a) write to bib file (bmc-mathphys only)
% @settings{label, options="nameyear"}
% b) uncomment next line
\nocite{label}

% or include bibliography directly:
% \begin{thebibliography}
% \bibitem{b1}
% \end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Figures                       %%
%%                               %%
%% NB: this is for captions and  %%
%% Titles. All graphics must be  %%
%% submitted separately and NOT  %%
%% included in the Tex document  %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Do not use \listoffigures as most will included as separate files

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Tables                        %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% Use of \listoftables is discouraged.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                               %%
%% Additional Files              %%
%%                               %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{backmatter}
\end{document}

### 2016-08-15 skimage_tomo.tex
New version with more files (figures and scripts to generate them)

@@
 \definecolor{listinggray}{gray}{0.1}
-\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
+\definecolor{lbcolor}{rgb}{0.9,0.92,0.95}
 \lstset{
@@
 dramatically over the last decade, from hours to
-seconds~\cite{Maire2014}. New modalities such as single-bunch
-imaging~\cite{Rack2014} provide a time resolution down to the nanosecond
+seconds~\citep{Maire2014}. New modalities such as single-bunch
+imaging~\citep{Rack2014} provide a time resolution down to the nanosecond
 for radiography. However, the time subsequently spent in processing the
@@
 needed to produce these data is not known beforehand, or might be altered
-due to artifacts~\cite{Marone2010}, or to an unforeseen evolution of
+due to artifacts~\citep{Marone2010}, or to an unforeseen evolution of
 the sample. Image processing necessarily involves trial and error phases
@@
 Several software applications and libraries are available to synchrotron
-users to process their images. ImageJ~\cite{Abramoff2004, Schneider2012}
-and its distribution Fiji~\cite{Schindelin2012} is a popular tool for 2-D
-and 3-D images, thanks to its intuitive menus and graphical tools, and
-the wealth of plugins contributed by a vivid
-community~\cite{Schindelin2015}. For 3-D images, commercial tools such as
-Avizo 3D software (TM) are appreciated for an intuitive graphical
+users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
+and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
+2-D and 3-D images, thanks to its intuitive menus and graphical tools,
+and the wealth of plugins contributed by a vivid
+community~\citep{Schindelin2015}. For 3-D images, commercial tools such
+as Avizo 3D software (TM) are appreciated for an intuitive graphical
 pipeline and advanced 3D visualization. Alternatively, the use of a
@@
 classical processing algorithms can be called from libraries -- hence
-limiting the programming task and the risk of bugs. Matlab (TM) and its image
-processing toolbox are popular in the academic community of computer
-vision and image processing. The Python language is widely used in the
-scientific world and in synchrotron facilitiies. As a general-purpose
-language, Python is used in synchrotrons for controlling device
-servers~\cite{pytango}, reconstructing tomography volumes from
-radiographies~\cite{Gursoy2014, Mirone2014}, and various data processing
-packages for macromolecular cristallography~\cite{Adams2010} or
-fluorescence analysis~\cite{pymca}.
+limiting the programming task and the risk of bugs. Matlab (TM) and its
+image processing toolbox are popular in the academic community of
+computer vision and image processing. The Python language is widely used
+in the scientific world and in synchrotron facilitiies. As a
+general-purpose language, Python is used in synchrotrons for controlling
+device servers~\citep{pytango}, reconstructing tomography volumes from
+radiographies~\citep{Gursoy2014, Mirone2014}, and various data
+processing packages for macromolecular cristallography~\citep{Adams2010},
+azimuthal integration of diffraction data~\citep{Ashiotis2015} or
+fluorescence analysis~\citep{pymca}.
 
-\texttt{scikit-image}~\cite{Vanderwalt2014} is a general-purpose image
+\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
 processing library for the Python language, and a component of the ecosystem of
 Python scientific modules commonly known as Scientific
-Python~\cite{Oliphant2007}. Like the rest of the ecosystem,
+Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
 \texttt{scikit-image} is released under a permissive open-source license and is
@@
 n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
-\texttt{NumPy} module~\cite{Vanderwalt2011}.
+\texttt{NumPy} module~\citep{Vanderwalt2011}.
 
@@
 from the features of the package alone, but also from the rich
-environment of Scientific Python~\cite{Oliphant2007, Perez2011}.
+environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
@@
 instructions and scripts, the most popular one in the scientific world is
-the IPython interpreter~\cite{Perez2007, Rossant2015}. IPython is an
+the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
 advanced interpreter, which integrates for example a debugger,
@@
 
-The Jupyter notebook~\cite{Kluyver2016} is a web application which has
+The Jupyter notebook~\citep{Kluyver2016} is a web application which has
 grown from the IPython project, although the two projects have now
@@
 
-\paragraph{NumPy arrays}
+\paragraph{NumPy arrays} are the cornerstone of the Scientific Python
+ecosystem, and of \texttt{scikit-image} operations in particular.
+Cropping or downsampling an image, or retrieving pixels corresponding to
+a given label in a segmentation are all one-liners NumPy code. To
+illustrate the compactness of NumPy code, modifying pixels values below a
+threshold can be written as
+\begin{lstlisting}
+im[im < 0.5] = 0
+\end{lstlisting}
+using the possibility to index arrays with boolean arrays, called
+\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
+making new copies of arrays whenever possible, which is a important
+requirement when dealing with the gigabyte-sized images of tomography.
+For example, cropping a subvolume as follows does not create a copy of the
+original array:
+\begin{lstlisting}
+sub_volume = im[100:-100, 100:-100, 100:-100]
+\end{lstlisting}
 
-- advanced operations in a compact form, at minimal memory consumption
+\paragraph{Visualization libraries.}
 
-- slicing to reduce memory cost
+Visualizing images is an important component of the image processing
+workflow, in order to verify the final result and to adjust the
+parameters of intermediate processing operations.
+\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
+library of the Python ecosystem. It can be used to visualize 2D data such
+as color or grayscale images, and 1D data such as contour lines, outlines
+of segmented regions, histograms of gray levels, etc. Although
+\texttt{matplotlib} has simple 3D plotting capabilities, it is
+recommended to use the \texttt{mayavi} module~\citep{Ramachandran2011}
+for applications requiring advanced 3D visualization, such as tomography. 
+\texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
+visualizing data passed as \texttt{numpy} arrays. For more advanced
+visualizations, a large majority of VTK capabilities can be accessed
+thanks to a pipeline API. A visualization pipeline can be designed either
+using the pipeline API, or graphically in the pipeline window.
+\texttt{mayavi} offers a good trade-off between simplicity of use for
+common operations, and more advanced possibilities, including responsive
+visualizations.
 
-- nD : 2D, 3D, ...
+speak about skimage's visualizer as well?
 
-\paragraph{Visualization libraries}
-
-\paragraph{Advanced toolkits for signal processing and data science}
+\paragraph{Advanced toolkits for signal processing and data science.}
 
@@
 processing, among many others. A very popular module is
-\texttt{scikit-learn}~\cite{Pedregosa2011}, a Python module for machine
+\texttt{scikit-learn}~\citep{Pedregosa2011}, a Python module for machine
 learning using \texttt{NumPy} arrays. If local features of an image
@@
 
-\begin{figure}
-    \centerline{\includegraphics[width=0.99\columnwidth]{mayavi_porous}}
+\begin{figure*}
+    \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
 \caption{\csentence{Sample figure title.}
@@
       should go here.}
-\end{figure}
+\end{figure*}
 
@@
 documentation. Functions of the API (define API here or above) are all
-documented using the same standard~\cite{Pawlik2015} as other major
+documented using the same standard~\citep{Pawlik2015} as other major
 Scientific Python packages. The standard include a description of all
@@
 In addition, a popular documentation tool is the graphical gallery of
-examples (url), a part of which is displayed in Fig.~\ref{fig:gallery}.
+examples (\url{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
 The principle of the gallery is to accelerate the learning curve of image
-processing, by displaying graphical examples of image processing
+processing, by showcasing graphical examples of image processing
 operations. Such examples are organized as an array of thumbnails with a
@@
 
-Finally, tutorials on \texttt{scikit-image} are available in various places,
-either as YouTube videos, or in the SciPy Lecture Notes~\cite{scipylecturenotes}, a comprehensive online book of Scientific Python tutorials.
+Finally, tutorials on \texttt{scikit-image} are available in various
+places, either as YouTube videos, or in the SciPy Lecture
+Notes~\citep{scipylecturenotes}, a comprehensive online book of Scientific
+Python tutorials.
 
@@
 \texttt{scikit-image} is developed by a diverse team of volunteers, with
-more than 170 developers that have contributed to the package. The
+more than 170 developers that have contributed to the package. The large
+number of developers and users is a key element of the sustainability of
+\texttt{scikit-image}. The
 development process takes place on the GitHub platform
@@
 A release cycle of one or two releases every year
-ensures that new features are proprosed to users on a regular basis.
+ensures that new features are proposed to users on a regular basis.
+
+\section*{Conclusion}
 
@@
 \section*{Competing interests}
-  The authors declare that they have no competing interests.
+: The authors declare that the research was conducted
+in the absence of any commercial or financial relationships that could be
+construed as a potential conflict of interest.
 
@@
 % b) uncomment next line
-\nocite{label}
+%\nocite{label}
 

### 2016-08-15 io.py

@@ -1,0 +1,4 @@
+from skimage import io
+im = io.imread('figure_gallery.png')
+io.imshow(im)
+

### 2016-08-15 io_coll.py

@@ -1,0 +1,6 @@
+>>> from skimage import io
+
+>>> image_collection = io.imread_collection('*.tif')
+>>> image_3d = image_collection.concatenate()
+>>> print(image_3d.shape)
+(800, 1024, 1024)

### 2016-08-15 process/ct_slic.py

@@ -1,0 +1,16 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+from skimage import io, segmentation
+
+im = io.imread('ct_wikipedia.jpg', as_grey=True)
+#pixels = segmentation.slic(im, n_segments=600, compactness=2.e-4)
+pixels = segmentation.felzenszwalb(im, scale=200)
+
+plt.figure(figsize=(5, 5))
+plt.imshow(segmentation.mark_boundaries(im, pixels))
+plt.axis('off')
+plt.tight_layout()
+plt.show()
+plt.savefig('super_pixels.png')
+

### 2016-08-15 process/denoising_demix2d.py

@@ -1,0 +1,12 @@
+import numpy as np
+from skimage import restoration, io
+import matplotlib.pyplot as plt
+
+dat = io.imread('phase_separation_insitu.png', as_grey=True)
+
+tv = restoration.denoise_tv_bregman(dat, weight=.8)
+
+l_r, l_c = dat.shape
+dat[:, l_c / 2:] = tv[:, l_c / 2:]
+
+plt.imsave('tv_denoising.png', dat[100:350, 245 - 150:245 + 150], cmap='gray', vmin=0.2, vmax=0.8)

### 2016-08-15 process/denoising_nlm.py

@@ -1,0 +1,12 @@
+import numpy as np
+from skimage import restoration, io, img_as_float
+import matplotlib.pyplot as plt
+
+dat = img_as_float(io.imread('raw_image.jpg'))
+
+nlm = restoration.denoise_nl_means(dat, h=0.1)
+
+l_r, l_c = dat.shape
+dat[:, l_c / 2:] = nlm[:, l_c / 2:]
+
+plt.imsave('nlm_denoising.png', dat[30:-30, 30:-30], cmap='gray', vmin=0.1, vmax=0.9)

### 2016-08-15 process/plot_random_walker_segmentation.py

@@ -1,0 +1,40 @@
+"""
+==========================
+Random walker segmentation
+==========================
+
+The random walker algorithm [1]_  determines the segmentation of an image from
+a set of markers labeling several phases (2 or more). An anisotropic diffusion
+equation is solved with tracers initiated at the markers' position. The local
+diffusivity coefficient is greater if neighboring pixels have similar values,
+so that diffusion is difficult across high gradients. The label of each unknown
+pixel is attributed to the label of the known marker that has the highest
+probability to be reached first during this diffusion process.
+
+In this example, two phases are clearly visible, but the data are too
+noisy to perform the segmentation from the histogram only. We determine
+markers of the two phases from the extreme tails of the histogram of gray
+values, and use the random walker for the segmentation.
+
+.. [1] *Random walks for image segmentation*, Leo Grady, IEEE Trans. Pattern
+       Anal. Mach. Intell. 2006 Nov; 28(11):1768-83
+
+"""
+import numpy as np
+import matplotlib.pyplot as plt
+
+from skimage.segmentation import random_walker
+from skimage.data import binary_blobs
+import skimage
+
+# Generate noisy synthetic data
+data = skimage.img_as_float(binary_blobs(length=128, seed=1))
+data += 0.35 * np.random.randn(*data.shape)
+markers = np.zeros(data.shape, dtype=np.uint)
+markers[data < -0.3] = 1
+markers[data > 1.3] = 2
+
+# Run random walker algorithm
+labels = random_walker(data, markers, beta=10, mode='bf')
+
+

### 2016-08-15 process/script_open_porosity.py

@@ -1,0 +1,39 @@
+import numpy as np
+from skimage import data, measure, morphology
+from scipy import ndimage
+
+im = data.binary_blobs(length=400, n_dim=3, volume_fraction=0.33, seed=0)
+mask = np.zeros(im.shape, dtype=np.bool)
+mask[200:, 200:, 200:] = True
+labels = ndimage.label(im)[0].astype(np.uint8)
+sizes = np.bincount(labels.ravel())
+order = np.argsort(sizes)
+biggest_label = order[-2]
+sorted_sizes = np.sort(sizes)[::-1]
+ratio = sorted_sizes[1] / float(sorted_sizes[1:].sum())
+print("ratio: ", ratio)
+print("nb of labels: ", labels.max())
+
+connected_phase = labels == biggest_label
+skel = morphology.skeletonize_3d(connected_phase)
+skel = morphology.binary_dilation(skel, selem=np.ones((3, 3, 3)))
+distance = ndimage.distance_transform_cdt(connected_phase).astype(np.float32)
+
+from mayavi import mlab
+fig = mlab.figure(bgcolor=(0, 0, 0))
+
+skel_src = mlab.pipeline.scalar_field(skel.astype(np.uint8))
+skel_src.image_data.point_data.add_array(distance.T.ravel())
+# We need to give a name to our new dataset.
+skel_src.image_data.point_data.get_array(1).name = 'distance'
+skel_src.update()
+skel_src2 = mlab.pipeline.set_active_attribute(skel_src,
+                                            point_scalars='scalar')
+skel_contour = mlab.pipeline.contour(skel_src2)
+skel_contour2 = mlab.pipeline.set_active_attribute(skel_contour,
+                                            point_scalars='distance')
+mlab.pipeline.surface(skel_contour2, colormap='hot')
+
+
+mlab.contour3d(connected_phase.astype(np.uint8), contours=[0.5], opacity=0.1, colormap='cool')
+mlab.outline()

### 2016-08-15 process/script_particles.py

@@ -1,0 +1,37 @@
+import numpy as np
+from skimage import segmentation, morphology, measure
+from mayavi import mlab
+
+
+def random_ellipses(l=256, number=30, size_fraction=0.1, seed=None):
+    rs = np.random.RandomState(seed)
+    im = np.zeros((l, l, l), dtype=np.uint8)
+    X, Y, Z = np.ogrid[:l, :l, :l]
+    x, y, z = rs.random_integers(0, l, 3 * number).reshape((3, number))
+    a, b, c = l * size_fraction / 2 * (rs.rand(3 * number).
+                            reshape((3, number))) + l * size_fraction / 2
+    for (xx, yy, zz, aa, bb, cc) in zip(x, y, z, a, b, c):
+        im += ((X - xx)**2 / aa**2 + (Y - yy)**2 / bb**2 + 
+                (Z - zz)**2 / cc**2) < 1
+    return segmentation.clear_border(im)
+
+
+im = random_ellipses(seed=0)
+labels = morphology.label(im)
+props = measure.regionprops(labels)
+vols = np.array([0] + [prop.extent for prop in props])
+color_by_extent = vols[labels]
+
+fig = mlab.figure(bgcolor=(0, 0, 0))
+src = mlab.pipeline.scalar_field(im)
+src.image_data.point_data.add_array(color_by_extent.T.ravel())
+# We need to give a name to our new dataset.
+src.image_data.point_data.get_array(1).name = 'extent'
+src.update()
+src2 = mlab.pipeline.set_active_attribute(src, point_scalars='scalar')
+contour = mlab.pipeline.contour(src2)
+contour2 = mlab.pipeline.set_active_attribute(contour, point_scalars='extent')
+mlab.pipeline.surface(contour2, colormap='gnuplot2')
+
+mlab.outline()
+mlab.show()

### 2016-08-15 process/script_porous.py

@@ -1,0 +1,59 @@
+import numpy as np
+from skimage import data, measure, morphology
+from scipy import ndimage
+
+im = data.binary_blobs(length=400, n_dim=3, volume_fraction=0.33, seed=0)
+mask = np.zeros(im.shape, dtype=np.bool)
+mask[200:, 200:, 200:] = True
+labels = ndimage.label(im)[0].astype(np.uint8)
+sizes = np.bincount(labels.ravel())
+order = np.argsort(sizes)
+biggest_label = order[-2]
+sorted_sizes = np.sort(sizes)[::-1]
+ratio = sorted_sizes[1] / float(sorted_sizes[1:].sum())
+print("ratio: ", ratio)
+print("nb of labels: ", labels.max())
+
+connected_phase = labels == biggest_label
+skel = morphology.skeletonize_3d(connected_phase)
+skel[mask] = 0
+skel = morphology.binary_dilation(skel, selem=np.ones((3, 3, 3)))
+distance = ndimage.distance_transform_cdt(connected_phase).astype(np.float32)
+distance[skel == 0] = 0
+
+from mayavi import mlab
+fig = mlab.figure(bgcolor=(0, 0, 0))
+labels[labels == biggest_label] = 0
+sizes[:2] = 0
+radii = sizes**0.33
+labels = radii[labels]
+labels[~mask] = 0
+im = (labels > 0).astype(np.uint8)
+
+src = mlab.pipeline.scalar_field(im)
+src.image_data.point_data.add_array(labels.T.ravel())
+# We need to give a name to our new dataset.
+src.image_data.point_data.get_array(1).name = 'label'
+src.update()
+src2 = mlab.pipeline.set_active_attribute(src,
+                                            point_scalars='scalar')
+contour = mlab.pipeline.contour(src2)
+contour2 = mlab.pipeline.set_active_attribute(contour,
+                                            point_scalars='label')
+mlab.pipeline.surface(contour2, colormap='cool')
+
+skel_src = mlab.pipeline.scalar_field(skel.astype(np.uint8))
+skel_src.image_data.point_data.add_array(distance.T.ravel())
+# We need to give a name to our new dataset.
+skel_src.image_data.point_data.get_array(1).name = 'distance'
+skel_src.update()
+skel_src2 = mlab.pipeline.set_active_attribute(skel_src,
+                                            point_scalars='scalar')
+skel_contour = mlab.pipeline.contour(skel_src2)
[…]

### 2016-08-16 skimage_tomo.tex
Fixed bibliography
New version of Fig. 3 + README

@@
 %\RequirePackage{natbib}
+\RequirePackage{hyperref}
 \RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
-\RequirePackage{hyperref}
 \usepackage[utf8]{inputenc} %unicode support
@@
       A short description of the figure content
-      should go here.}
+  should go here. \label{fig:tomo_gallery}}
 \end{figure*}
+
+\texttt{scikit-image} offers all the classical operations of image
+processing, such as exposure and color adjustment, filtering,
+segmentation, features extraction, geometric transformations or
+measurements of region characteristics. For these
+different categories, the package includes both standard generic
+operations and more advanced algorithms. A sample of
+\texttt{scikit-image} capabilities is given in
+Fig.~\ref{fig:tomo_gallery}.
 
@@
 % b) uncomment next line
-%\nocite{label}
+\nocite{label}
 

### 2016-08-16 io_coll.py
Prefer functions over object methods

@@ -1,6 +1,6 @@
 >>> from skimage import io
 
 >>> image_collection = io.imread_collection('*.tif')
->>> image_3d = image_collection.concatenate()
+>>> image_3d = io.concatenate(image_collection)
 >>> print(image_3d.shape)
 (800, 1024, 1024)

### 2016-08-16 skimage_tomo.tex
Fix Stéfan's name
Update my affiliation

--- 2016-08-15 skimage_tomo.tex
@@
    email={stefanv@berkeley.edu}
-]{\fnm{Stéfan} \snm{Van der Walt}}
+]{\fnm{Stéfan} \snm{van der Walt}}
 
@@
 \address[id=aff2]{%
-  \orgname{Life Sciences Computation Centre, University of Melbourne},
-  %\street{D\"{u}sternbrooker Weg 20},
-  %\postcode{24105}
-  \city{Melbourne},
+  \orgname{Victorian Life Sciences Computation Initiative, University of Melbourne},
+  %\street{700 Swanston St},
+  %\postcode{3053}
+  \city{Carlton, VIC},
   \cny{Australia}

### 2016-08-16 skimage_tomo.tex
Various wording suggestions

@@
 computer vision and image processing. The Python language is widely used
-in the scientific world and in synchrotron facilitiies. As a
-general-purpose language, Python is used in synchrotrons for controlling
-device servers~\citep{pytango}, reconstructing tomography volumes from
-radiographies~\citep{Gursoy2014, Mirone2014}, and various data
+in the scientific world and in synchrotron facilities. As a
+general-purpose language, Python is used in synchrotrons to control
+device servers~\citep{pytango}, to reconstruct tomography volumes from
+radiographs~\citep{Gursoy2014, Mirone2014}, and in data
 processing packages for macromolecular cristallography~\citep{Adams2010},
@@
 \texttt{scikit-image} is released under a permissive open-source license and is
-available free of charge. \texttt{scikit-image} is compatible with both 2-D and
+available free of charge. Most of \texttt{scikit-image} is compatible with both 2-D and
 3-D images, so that it can be used for a large number of imaging modalities,
@@
 for X-ray imaging, but rather to explain the rationale behind the package, and
-what can be done with \texttt{scikit-image}.
+provide various examples of its capabilities.
 
@@
 
-Image are manipulated as numerical arrays of uniform
+Images are manipulated as numerical arrays of uniform
 data type, a format that guarantees a fast access to the computer memory. The
@@
 In image processing, one of the first tasks is therefore to generate
-\texttt{NumPy} arrays, which is often done by reading data from files. Let us
+\texttt{NumPy} arrays, which is often done by reading data from files. We
 read one 2-D image from a file and display it with the following lines of code:
@@
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
-ecosystem are used for a typical image processing workflow.
+ecosystem combine into a sophisticated image processing workflow.
 

### 2016-08-16 skimage_tomo.tex
Suggest other IDEs also. Notes about notebooks

@@
 the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
-advanced interpreter, which integrates for example a debugger,
-introspection and profiling methods, and online help. Several IDEs
-(Integrated Development Environment) integrate the IPython interpreter,
-together with other components such as a text editor. For example, Spyder 
-is a popular IDE (see Fig.~\ref{fig:spyder}).
+advanced interpreter, which integrates syntax highlighting, text auto-completion,
+a debugger,
+introspection and profiling methods, and online help. Several
+Integrated Development Environments (IDEs) include IPython,
+together with other components such as a text editor. Notable examples
+include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.
 
@@
 
-The Jupyter notebook~\citep{Kluyver2016} is a web application which has
-grown from the IPython project, although the two projects have now
-diverged. Jupyter notebooks provide an interactive development
-environment within an Internet browser, where live code can be enriched
-by explanatory text, equations and visualizations (figure or not??).
+The Jupyter notebook~\citep{Kluyver2016} is a web application that grew
+from the IPython project. Jupyter notebooks provide an interactive development
+environment within a web browser, where live code can be enriched
+by explanatory text, equations and visualizations (FIGURE).
+(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
 

### 2016-08-16 skimage_tomo.tex
Wording fixes

@@
 of segmented regions, histograms of gray levels, etc. Although
-\texttt{matplotlib} has simple 3D plotting capabilities, it is
-recommended to use the \texttt{mayavi} module~\citep{Ramachandran2011}
+\texttt{matplotlib} has simple 3D plotting capabilities, we
+recommend using the \texttt{mayavi} module~\citep{Ramachandran2011}
 for applications requiring advanced 3D visualization, such as tomography. 
@@
 visualizations, a large majority of VTK capabilities can be accessed
-thanks to a pipeline API. A visualization pipeline can be designed either
-using the pipeline API, or graphically in the pipeline window.
+thanks to a pipeline API.
 \texttt{mayavi} offers a good trade-off between simplicity of use for

### 2016-08-16 skimage_tomo.tex
Remove suggestion about skimage.viewer
That module definitely needs some love. I don't think it's ready for
mention in a publication.
Various typo/wording fixes

@@
 
-speak about skimage's visualizer as well?
-
 \paragraph{Advanced toolkits for signal processing and data science.}
@@
 are almost perfectly compatible, thanks to the shared use of NumPy arrays
-and common development practices, although they are developed in parallel
-by different teams.
+and common development practices (although they are developed in parallel
+by different teams).
 
@@
 input and output variables and their data type, together with
-explainations on what the function does and how to use it. Functions
+explanations on what the function does and how to use it. Function
 documentation is accessed either online, or within the development
@@
 operations. Such examples are organized as an array of thumbnails with a
-short title (see Fig.~\ref{fig:gallery} left). Thumbnails are links to
+short title (see Fig.~\ref{fig:gallery} left). These thumbnails link to
 the webpage of the corresponding example, which features a mini-tutorial

### 2016-08-16 skimage_tomo.tex
Some progress on image capabilities section

--- 2016-08-16 skimage_tomo.tex
@@
    email={stefanv@berkeley.edu}
-]{\fnm{Stéfan} \snm{van der Walt}}
+]{\fnm{Stéfan} \snm{Van der Walt}}
 
@@
 \address[id=aff2]{%
-  \orgname{Victorian Life Sciences Computation Initiative, University of Melbourne},
-  %\street{700 Swanston St},
-  %\postcode{3053}
-  \city{Carlton, VIC},
+  \orgname{Life Sciences Computation Centre, University of Melbourne},
+  %\street{D\"{u}sternbrooker Weg 20},
+  %\postcode{24105}
+  \city{Melbourne},
   \cny{Australia}
@@
 computer vision and image processing. The Python language is widely used
-in the scientific world and in synchrotron facilities. As a
-general-purpose language, Python is used in synchrotrons to control
-device servers~\citep{pytango}, to reconstruct tomography volumes from
-radiographs~\citep{Gursoy2014, Mirone2014}, and in data
+in the scientific world and in synchrotron facilitiies. As a
+general-purpose language, Python is used in synchrotrons for controlling
+device servers~\citep{pytango}, reconstructing tomography volumes from
+radiographies~\citep{Gursoy2014, Mirone2014}, and various data
 processing packages for macromolecular cristallography~\citep{Adams2010},
@@
 \texttt{scikit-image} is released under a permissive open-source license and is
-available free of charge. Most of \texttt{scikit-image} is compatible with both 2-D and
+available free of charge. \texttt{scikit-image} is compatible with both 2-D and
 3-D images, so that it can be used for a large number of imaging modalities,
@@
 for X-ray imaging, but rather to explain the rationale behind the package, and
-provide various examples of its capabilities.
+what can be done with \texttt{scikit-image}.
 
@@
 
-Images are manipulated as numerical arrays of uniform
+Image are manipulated as numerical arrays of uniform
 data type, a format that guarantees a fast access to the computer memory. The
@@
 In image processing, one of the first tasks is therefore to generate
-\texttt{NumPy} arrays, which is often done by reading data from files. We
+\texttt{NumPy} arrays, which is often done by reading data from files. Let us
 read one 2-D image from a file and display it with the following lines of code:
@@
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
-ecosystem combine into a sophisticated image processing workflow.
+ecosystem are used for a typical image processing workflow.
 
@@
 the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
-advanced interpreter, which integrates syntax highlighting, text auto-completion,
-a debugger,
-introspection and profiling methods, and online help. Several
-Integrated Development Environments (IDEs) include IPython,
-together with other components such as a text editor. Notable examples
-include Spyder (Fig.~\ref{fig:spyder}), PyCharm, and Visual Studio Code.
+advanced interpreter, which integrates for example a debugger,
+introspection and profiling methods, and online help. Several IDEs
+(Integrated Development Environment) integrate the IPython interpreter,
+together with other components such as a text editor. For example, Spyder 
+is a popular IDE (see Fig.~\ref{fig:spyder}).
 
@@
 
-The Jupyter notebook~\citep{Kluyver2016} is a web application that grew
-from the IPython project. Jupyter notebooks provide an interactive development
-environment within a web browser, where live code can be enriched
-by explanatory text, equations and visualizations (FIGURE).
-(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
+The Jupyter notebook~\citep{Kluyver2016} is a web application which has
+grown from the IPython project, although the two projects have now
+diverged. Jupyter notebooks provide an interactive development
+environment within an Internet browser, where live code can be enriched
+by explanatory text, equations and visualizations (figure or not??).
 
@@
 of segmented regions, histograms of gray levels, etc. Although
-\texttt{matplotlib} has simple 3D plotting capabilities, we
-recommend using the \texttt{mayavi} module~\citep{Ramachandran2011}
+\texttt{matplotlib} has simple 3D plotting capabilities, it is
+recommended to use the \texttt{mayavi} module~\citep{Ramachandran2011}
 for applications requiring advanced 3D visualization, such as tomography. 
@@
 visualizations, a large majority of VTK capabilities can be accessed
-thanks to a pipeline API.
+thanks to a pipeline API. A visualization pipeline can be designed either
+using the pipeline API, or graphically in the pipeline window.
 \texttt{mayavi} offers a good trade-off between simplicity of use for
@@
       A short description of the figure content
-      should go here.}
+  should go here. \label{fig:tomo_gallery}}
 \end{figure*}
+
+\texttt{scikit-image} offers all the classical operations of image
+processing, such as exposure and color adjustment, filtering,
+segmentation, features extraction, geometric transformations or
+measurements of region characteristics. For these
+different categories, the package includes both standard generic
+operations and more advanced algorithms. A sample of
+\texttt{scikit-image} capabilities is given in
+Fig.~\ref{fig:tomo_gallery}.
+
+Tomographic images often suffer from artifacts or poor signal-to-noise
+ratio. Several denoising filters are available for image restoration,
+from general-purpose filters such as median and bilateral filters, to more
+specific filters. Total-variation denoising~\citep{Chambolle2004,
+Getreuer2012} is well-suited to restore
+piecewise-constant images, such as images with a small number of phases
+encountered in materials science~\citep{Bouttes2015}. Conversely, images
+with a fine-grained texture are better preserved with non-local means
+denoising~\citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
 

### 2016-08-16 skimage_tomo.tex

--- 2016-08-16 skimage_tomo.tex
@@
 
+Tomographic images often suffer from artifacts or poor signal-to-noise
+ratio. Several denoising filters are available for image restoration,
+from general-purpose filters such as median and bilateral filters, to more
+specific filters. Total-variation denoising~\citep{Chambolle2004,
+Getreuer2012} is well-suited to restore
+piecewise-constant images, such as images with a small number of phases
+encountered in materials science~\citep{Bouttes2015}. Conversely, images
+with a fine-grained texture are better preserved with non-local means
+denoising~\citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
+
 \paragraph{Performance}

### 2016-08-16 skimage_tomo.tex
Continued section on image processing capabilities

@@
 \startlocaldefs
+\newcommand{\emma}[1]{{\color{blue}{#1}}}
+
 \endlocaldefs
@@
 general-purpose language, Python is used in synchrotrons to control
-device servers~\citep{pytango}, to reconstruct tomography volumes from
+device servers~\citep{pytango}, to access raw data of X-ray
+detectors~\citep{Knudsen2013}, to reconstruct tomography volumes from
 radiographs~\citep{Gursoy2014, Mirone2014}, and in data
@@
 
+\emma{Insert paragraph on features detection here? Juan?} Diffraction
+peaks in 2D diffraction images can be extracted using blob detection
+methods~\citep{Ashiotis2015}, such as the Laplacian of Gaussian method
+(see Fig.~\ref{fig:tomo_gallery}).
+
+Segmentation of regions of interest can be achieved using different
+strategies, depending on the characteristics of the image. Images with a
+clear contrast between regions can be segmented automatically thanks to
+several thresholding algorithms, including an adaptive local thresholding
+algorithm aimed at images with contrast variations. Super-pixel
+algorithms~\citep{Felzenszwalb2004, Achanta2012} (see
+Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
+super-pixels, by grouping pixels that are close together both in color-
+and direct space. Region-growing algorithms, such as the morphological
+watershed or the random walker~\citep{Grady2006}, propagate the labels
+of user-defined markers through the image (see
+Fig.~\ref{fig:tomo_gallery}). The active contour
+algorithm~\citep{Kass1988} fits snake contours to features of the
+image, such as edges or high-brightness regions.
+
+The characteristics of labeled regions (particles, porosities, organs,
+\dots) resulting from a segmentation can be measured using the
+\texttt{measure} submodule. The different connected components (e.g.
+bubbles or non-touching particles) of a binary image are labeled with the
+\texttt{measure.label} function. Properties of labeled regions such as
+size, extent, center of mass or mean intensity value are accessed with
+\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery}). Local
+characteristics of a region can be retrieved as well:
+Fig.~\ref{fig:tomo_gallery} shows how the local diameter of open
+porosity is measured by combining a skeletonization of the porosity
+channels, and the distance transform to the other phase measured on the
+skeleton.
+
 \paragraph{Performance}

### 2016-08-16 skimage_tomo.tex
More progress on image processing capabilities section

@@
 
-\paragraph{Performance}
+\paragraph{Performance.}
+
+Given the large size of tomography datasets, the speed of execution of image
+processing operations is a critical issue. \texttt{scikit-image} relies mostly
+on calls to \texttt{NumPy} operations, with most of them that are performed in
+optimized compiled code (C or Fortran). Performance-critical parts of the code
+that cannot call efficient \texttt{NumPy} code are implemented in
+\texttt{Cython}. \texttt{Cython}~\citep{Behnel2011} is an extension of the
+Python language that supports explicit type declarations, and is compiled
+directly to C.
+
+However, basic \texttt{scikit-image} code runs on a single core. Computing
+workstations and servers used for X-ray imaging typically have several tens of
+cores. Parallelization of the computing workflow can be achieved in different
+ways. The most trivial parallelization scheme consists in applying the same
+workflow to different images, on different cores. However, finer-grained
+parallelization is preferable when prototyping the processing workflow.
+
+\emma{Juan or Stéfan, can you add something about dask?}
+
+Prototyping the image processing workflow requires several trial and error
+executions of scripts containing different operations. The \texttt{joblib}
+module provides a caching mechanism that avoids the repetition of function
+calls, if their arguments have not changed:
+\begin{lstlisting}
+>>> from skimage import filters, data
+>>> from joblib import Memory
+>>> mem = Memory(cachedir='/tmp/joblib')
+>>> median = mem.cache(filters.median)
+>>> im = data.camera()
+>>> filtered_im = median(im, np.ones((3, 3)))
+__________________________
+[Memory] Calling skimage.filters.rank.generic.median...
+median(array([[156, ..., 152],
+       ..., 
+       [121, ..., 111]], dtype=uint8), array([[ 1.,  1.,  1.],
+       [ 1.,  1.,  1.],
+       [ 1.,  1.,  1.]]))
+__________________________median - 0.0s, 0.0min
+>>> filtered_again = median(im, np.ones((3, 3)))
+>>> # the above call did not trigger an evaluation
+\end{lstlisting}
+
+Finally, let us note that the biggest performance improvements often come from
+the improvement of algorithms (as opposed to computing architectures only). For
+example, non-local means denoising~\citep{Buades2005} is a costly operation,
+since it requires several nested loops, on all pixels and on neighboring
+patches to be compared with the pixel-centered patch. Thanks to the
+implementation of a more recent algorithm~\citep{Darbon2008} that modifies the
+internal organization of loops, it was possible to gain a factor of 5 to 10.
+The large size of the \texttt{scikit-image} community ensures that possible
+algorithmic improvements are discussed regularly.
 

### 2016-08-17 skimage_tomo.tex
Some text for captions + small changes in ecosystem figure

@@
     \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
-\caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
- The gallery of examples consists of an array of thumbnails (left part),
- which link to example webpages, each centerered on a specific image
- processing task. Each webpage includes Python code generating a figure,
- the figure itself, as well as a short tutorial explaining the image
- processing operations and the code. \label{fig:ecosystem}}
+    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
+	ecosystem}. Images are opened from files as \texttt{NumPy}
+	arrays. Functions of \texttt{scikit-image} transform image arrays
+	into other arrays with the same dimensions, or into arrays of
+	numbers corresponding to features of the image. The output of
+	scikit-image functions can be passed to other Python modules
+	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
+	\texttt{scikit-learn}. Image-shaped arrays are transformed into
+	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
+	(3D). A variety of environments is available for code development
+	and execution, from classical IDEs to Jupyter notebooks.
+    \label{fig:ecosystem}}
 \end{figure*}
@@
     \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
-\caption{\csentence{Sample figure title.}
-      A short description of the figure content
-  should go here. \label{fig:spyder}}
+    \caption{\csentence{The Spyder IDE} integrates a text editor (with
+	syntax highlighting), the IPython interpreter, as well as a panel
+	for code introspection (online help, variable explorer, \dots).
+ \label{fig:spyder}}
 \end{figure*}

### 2016-08-17 skimage_tomo.tex
Caption of fig 3 + some work on first steps section

@@
 
-\title{scikit-image, a Python library for 2D and 3D image
-processing}
+\title{Analyzing tomographic images in Python with scikit-image}
 
@@
 
+\textcolor{blue}{text to be written to explain the following snippets of
+code}
+
+\begin{lstlisting}
+>>> from skimage import filters
+>>> im_gaussian = filters.gaussian(im)
+\end{lstlisting}
+
+\begin{lstlisting}
+>>> im_gaussian = filters.gaussian(im, sigma=3, mode='wrap')
+\end{lstlisting}
+
 \begin{figure*}
@@
 \end{figure*}
+
+\begin{lstlisting}
+>>> from skimage import morphology
+>>> labels = morphology.watershed(im, markers)
+\end{lstlisting}
+
+Most functions take indifferently 2-D or 3-D images as arguments, so that
+the same functions can be used to process tomography and microscopy
+images. Only a few functions do not support 3-D images and raise an error
+when passed a 3-D argument:
+
+\begin{lstlisting}
+>>> filters.prewitt(im)
+[...]
+ValueError: The parameter `image` must be a 2-dimensional array
+\end{lstlisting}
 
@@
     \centerline{\includegraphics[width=0.99\textwidth]{tomo_gallery}}
-\caption{\csentence{Sample figure title.}
-      A short description of the figure content
-  should go here. \label{fig:tomo_gallery}}
+    \caption{\csentence{Typical image processing operations with
+	\texttt{scikit-image}.} From left to right and top to bottom.
+	Data are syntheric, unless stated otherwise.
+	\textbf{Filtering -} Top: non-local means denoising of an image
+	with a fine-grained texture, acquired by \emph{in situ}
+	synchrotron microtomography during
+	glass melting~\citep{Gouillart2012}. Bottom: total-variation
+	denoising of an image with two phases, corresponding to
+	phase-separating silicate melts observed by \emph{in situ
+	tomography}~\citep{Bouttes2015}.
+	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
+	public domain), blob detection using the
+	Laplacian of Gaussian method. Bottom: ??
+	\textbf{Segmentation - } Top: super-pixel segmentation
+	of a CT slice of the human head~\citep{tomo_wikipedia}, using
+	Felzenszwalb's algorithm~\citep{Felzenszwalb2004}. Bottom: random
+	walker segmentation (right) of noisy image (top-left corner), using
+	histogram-determined markers (bottom-left corner).
+	\textbf{Measures -} Top: visualization of local diameter
+	(color-coded on the skeleton curve) of an
+	interconnected phase (represented in violet).  Bottom: particles color-coded according
+	to their extent.
+\label{fig:tomo_gallery}}
 \end{figure*}

### 2016-08-17 skimage_tomo.tex
More work on first steps section

@@
 
+\begin{figure*}
+    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
+    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
+	ecosystem}. Images are opened from files as \texttt{NumPy}
+	arrays. Functions of \texttt{scikit-image} transform image arrays
+	into other arrays with the same dimensions, or into arrays of
+	numbers corresponding to features of the image. The output of
+	scikit-image functions can be passed to other Python modules
+	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
+	\texttt{scikit-learn}. Image-shaped arrays are transformed into
+	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
+	(3D). A variety of environments is available for code development
+	and execution, from classical IDEs to Jupyter notebooks.
+    \label{fig:ecosystem}}
+\end{figure*}
+
 Images are manipulated as numerical arrays of uniform
@@
 
-\textcolor{blue}{text to be written to explain the following snippets of
-code}
-
+\texttt{scikit-image} has a very simple API, based almost only on
+functions. Most functions take an image (\emph{i.e} a multi-dimensional
+array) as input parameter:
 \begin{lstlisting}
@@
 
+Optional parameters can be passed as Python's \emph{keyword arguments},
+in addition to the image parameter.
 \begin{lstlisting}
@@
 \end{lstlisting}
-
-\begin{figure*}
-    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
-    \caption{\csentence{\texttt{scikit-image} and the Scientific Python
-	ecosystem}. Images are opened from files as \texttt{NumPy}
-	arrays. Functions of \texttt{scikit-image} transform image arrays
-	into other arrays with the same dimensions, or into arrays of
-	numbers corresponding to features of the image. The output of
-	scikit-image functions can be passed to other Python modules
-	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
-	\texttt{scikit-learn}. Image-shaped arrays are transformed into
-	visualizations with \texttt{matplotlib} (2D) or \texttt{Mayavi}
-	(3D). A variety of environments is available for code development
-	and execution, from classical IDEs to Jupyter notebooks.
-    \label{fig:ecosystem}}
-\end{figure*}
-
+A few functions require several arrays to be passed, such as the
+watershed segmentation algorithm that takes as parameters the image to be
+segmented, and an image of markers from which labels are propagated:
 \begin{lstlisting}
@@
 \end{lstlisting}
+Therefore, the image processing workflow can be considered as a directed graph
+(\textcolor{blue}{or is it a tree?})
+(rather than a linear pipeline), where nodes are image-shaped arrays, and
+edges are functions of \texttt{scikit-image} transforming the arrays (see
+Fig.~\ref{fig:ecosystem}).
 
@@
 when passed a 3-D argument:
-
 \begin{lstlisting}

### 2016-08-19 skimage_tomo.tex
Abstract + completed section first steps

@@
 %\RequirePackage{natbib}
-\RequirePackage{hyperref}
+\RequirePackage[breaklinks=true]{hyperref}
 \RequirePackage[authoryear]{natbib}% uncomment this for author-year bibliography
@@
 
-\title{Analyzing tomographic images in Python with scikit-image}
+\title{Analyzing X-ray images in Python with scikit-image}
 
@@
 \begin{abstract} % abstract
-\parttitle{First part title} %if any
-Text for this section.
+    The exploration and processing of images is a vital aspect of the
+    scientific workflow of different X-ray imaging modalities. Users
+    require tools combining interactivity, versatility, and performance.
 
-\parttitle{Second part title} %if any
-Text for this section.
+    \texttt{scikit-image} is an open-source image processing toolkit for
+    the Python language, that supports a large variety of file formats
+    and is compatible with 2-D and 3-D images. The toolkit exposes a
+    simple programming interface, corresponding to functions performing
+    operations on images, and different thematic modules that group these
+    functions according to their purpose, such as image restoration,
+    segmentation, measurements, etc. \texttt{scikit-image} users benefit
+    from the rich ecosystem of Python for science, with powerful
+    visualization libraries or machine learning toolkits.
+    \texttt{scikit-image} combines a gentle
+    learning curve, versatile image processing capabilities, and the
+    scalable performances required for the high-throughput analysis of
+    X-ray imaging data.
+
 \end{abstract}
@@
 dramatically over the last decade, from hours to
-seconds~\citep{Maire2014}. New modalities such as single-bunch
-imaging~\citep{Rack2014} provide a time resolution down to the nanosecond
+seconds \citep{Maire2014}. New modalities such as single-bunch
+imaging \citep{Rack2014} provide a time resolution down to the nanosecond
 for radiography. However, the time subsequently spent in processing the
@@
 needed to produce these data is not known beforehand, or might be altered
-due to artifacts~\citep{Marone2010}, or to an unforeseen evolution of
+due to artifacts \citep{Marone2010}, or to an unforeseen evolution of
 the sample. Image processing necessarily involves trial and error phases
@@
 Several software applications and libraries are available to synchrotron
-users to process their images. ImageJ~\citep{Abramoff2004, Schneider2012}
-and its distribution Fiji~\citep{Schindelin2012} is a popular tool for
+users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
+and its distribution Fiji \citep{Schindelin2012} is a popular tool for
 2-D and 3-D images, thanks to its intuitive menus and graphical tools,
 and the wealth of plugins contributed by a vivid
-community~\citep{Schindelin2015}. For 3-D images, commercial tools such
+community \citep{Schindelin2015}. For 3-D images, commercial tools such
 as Avizo 3D software (TM) are appreciated for an intuitive graphical
@@
 general-purpose language, Python is used in synchrotrons to control
-device servers~\citep{pytango}, to access raw data of X-ray
-detectors~\citep{Knudsen2013}, to reconstruct tomography volumes from
-radiographs~\citep{Gursoy2014, Mirone2014}, and in data
-processing packages for macromolecular cristallography~\citep{Adams2010},
-azimuthal integration of diffraction data~\citep{Ashiotis2015} or
-fluorescence analysis~\citep{pymca}.
+device servers \citep{pytango}, to access raw data of X-ray
+detectors \citep{Knudsen2013}, to reconstruct tomography volumes from
+radiographs \citep{Gursoy2014, Mirone2014}, and in data
+processing packages for macromolecular cristallography \citep{Adams2010},
+azimuthal integration of diffraction data \citep{Ashiotis2015} or
+fluorescence analysis \citep{pymca}.
 
-\texttt{scikit-image}~\citep{Vanderwalt2014} is a general-purpose image
+\texttt{scikit-image} \citep{Vanderwalt2014} is a general-purpose image
 processing library for the Python language, and a component of the ecosystem of
 Python scientific modules commonly known as Scientific
-Python~\citep{Oliphant2007}. Like the rest of the ecosystem,
+Python \citep{Oliphant2007}. Like the rest of the ecosystem,
 \texttt{scikit-image} is released under a permissive open-source license and is
@@
 such as microscopy, radiography or tomography. In this article, we explain how
-\texttt{scikit-image} can be used for processing data acquired in synchrotron
-imaging experiments, with a strong focus on microtomography 3-D images. This
+\texttt{scikit-image} can be used for processing data acquired in X-ray
+imaging experiments, with a focus on microtomography 3-D images. This
 article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
@@
 n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
-\texttt{NumPy} module~\citep{Vanderwalt2011}.
+\texttt{NumPy} module \citep{Vanderwalt2011}.
 
@@
 Python code. Note that functions (such as \texttt{imread} to read an image
-file, or \texttt{imshow} to display an image) are found in submodules of
-\texttt{skimage}, such as \texttt{io}.
+file, or \texttt{imshow} to display an image) are found in thematic submodules of
+\texttt{skimage}, such as \texttt{io} for Input/Output.
 
@@
 
-\texttt{scikit-image} has a very simple API, based almost only on
+\texttt{scikit-image} has a very simple Application Programming Interface
+(API), based almost only on
 functions. Most functions take an image (\emph{i.e} a multi-dimensional
@@
 Therefore, the image processing workflow can be considered as a directed graph
-(\textcolor{blue}{or is it a tree?})
-(rather than a linear pipeline), where nodes are image-shaped arrays, and
+(a richer structure than a linear pipeline), where nodes are image-shaped arrays, and
 edges are functions of \texttt{scikit-image} transforming the arrays (see
@@
 
+Another type of functions returns numerical value(s) that do not
+correspond to image objects, such as pixel coordinates of objects of
+interest or statistical
+information about the image:
+\begin{lstlisting}
+>>> from skimage import exposure
+>>> counts, bins = exposure.histogram(im)
+>>> counts.shape
+(256,)
+\end{lstlisting}
+
 \section*{The Python ecosystem}
@@
 from the features of the package alone, but also from the rich
-environment of Scientific Python~\citep{Oliphant2007, Perez2011}.
+environment of Scientific Python \citep{Oliphant2007, Perez2011}.
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
@@
 instructions and scripts, the most popular one in the scientific world is
-the IPython interpreter~\citep{Perez2007, Rossant2015}. IPython is an
+the IPython interpreter \citep{Perez2007, Rossant2015}. IPython is an
 advanced interpreter, which integrates syntax highlighting, text auto-completion,
@@
 
-The Jupyter notebook~\citep{Kluyver2016} is a web application that grew
+The Jupyter notebook \citep{Kluyver2016} is a web application that grew
 from the IPython project. Jupyter notebooks provide an interactive development
@@
 parameters of intermediate processing operations.
-\texttt{matplotlib}~\citep{Hunter2007} is the most popular 2D plotting
+\texttt{matplotlib} \citep{Hunter2007} is the most popular 2D plotting
 library of the Python ecosystem. It can be used to visualize 2D data such
@@
 \texttt{matplotlib} has simple 3D plotting capabilities, we
-recommend using the \texttt{mayavi} module~\citep{Ramachandran2011}
+recommend using the \texttt{mayavi} module \citep{Ramachandran2011}
 for applications requiring advanced 3D visualization, such as tomography. 
@@
 processing, among many others. A very popular module is
-\texttt{scikit-learn}~\citep{Pedregosa2011}, a Python module for machine
+\texttt{scikit-learn} \citep{Pedregosa2011}, a Python module for machine
 learning using \texttt{NumPy} arrays. If local features of an image
@@
 	synchrotron microtomography during
-	glass melting~\citep{Gouillart2012}. Bottom: total-variation
+	glass melting \citep{Gouillart2012}. Bottom: total-variation
 	denoising of an image with two phases, corresponding to
 	phase-separating silicate melts observed by \emph{in situ
-	tomography}~\citep{Bouttes2015}.
+	tomography} \citep{Bouttes2015}.
 	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
@@
 	\textbf{Segmentation - } Top: super-pixel segmentation
-	of a CT slice of the human head~\citep{tomo_wikipedia}, using
-	Felzenszwalb's algorithm~\citep{Felzenszwalb2004}. Bottom: random
+	of a CT slice of the human head \citep{tomo_wikipedia}, using
+	Felzenszwalb's algorithm \citep{Felzenszwalb2004}. Bottom: random
 	walker segmentation (right) of noisy image (top-left corner), using
@@
 from general-purpose filters such as median and bilateral filters, to more
-specific filters. Total-variation denoising~\citep{Chambolle2004,
+specific filters. Total-variation denoising \citep{Chambolle2004,
 Getreuer2012} is well-suited to restore
 piecewise-constant images, such as images with a small number of phases
-encountered in materials science~\citep{Bouttes2015}. Conversely, images
+encountered in materials science \citep{Bouttes2015}. Conversely, images
 with a fine-grained texture are better preserved with non-local means
-denoising~\citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
+denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
 
@@
 peaks in 2D diffraction images can be extracted using blob detection
-methods~\citep{Ashiotis2015}, such as the Laplacian of Gaussian method
+methods \citep{Ashiotis2015}, such as the Laplacian of Gaussian method
 (see Fig.~\ref{fig:tomo_gallery}).
@@
 algorithm aimed at images with contrast variations. Super-pixel
-algorithms~\citep{Felzenszwalb2004, Achanta2012} (see
+algorithms \citep{Felzenszwalb2004, Achanta2012} (see
 Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
@@
 and direct space. Region-growing algorithms, such as the morphological
-watershed or the random walker~\citep{Grady2006}, propagate the labels
+watershed or the random walker \citep{Grady2006}, propagate the labels
 of user-defined markers through the image (see
 Fig.~\ref{fig:tomo_gallery}). The active contour
-algorithm~\citep{Kass1988} fits snake contours to features of the
+algorithm \citep{Kass1988} fits snake contours to features of the
 image, such as edges or high-brightness regions.
@@
 that cannot call efficient \texttt{NumPy} code are implemented in
-\texttt{Cython}. \texttt{Cython}~\citep{Behnel2011} is an extension of the
+\texttt{Cython}. \texttt{Cython} \citep{Behnel2011} is an extension of the
 Python language that supports explicit type declarations, and is compiled
@@
 the improvement of algorithms (as opposed to computing architectures only). For
-example, non-local means denoising~\citep{Buades2005} is a costly operation,
+example, non-local means denoising \citep{Buades2005} is a costly operation,
 since it requires several nested loops, on all pixels and on neighboring
 patches to be compared with the pixel-centered patch. Thanks to the
-implementation of a more recent algorithm~\citep{Darbon2008} that modifies the
+implementation of a more recent algorithm \citep{Darbon2008} that modifies the
 internal organization of loops, it was possible to gain a factor of 5 to 10.
@@
 documentation. Functions of the API (define API here or above) are all
-documented using the same standard~\citep{Pawlik2015} as other major
+documented using the same standard \citep{Pawlik2015} as other major
 Scientific Python packages. The standard include a description of all
@@
 places, either as YouTube videos, or in the SciPy Lecture
-Notes~\citep{scipylecturenotes}, a comprehensive online book of Scientific
+Notes \citep{scipylecturenotes}, a comprehensive online book of Scientific
 Python tutorials.

### 2016-08-19 skimage_tomo.tex
Iteration on performance + doc

@@
 intensity characteristics of segmented particles) are extracted with
-functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}, it
+functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}), it
 is then possible to use a \emph{classification} algorithm of
@@
 
-The modularity of the Scientific Python ecosystem may look
+The modularity of the Scientific Python ecosystem may be
 confusing at first sight. Nevertheless, core modules of this ecosystem
@@
 and common development practices (although they are developed in parallel
-by different teams).
+by different teams). Several integrated distributions, such as Anaconda
+or Canopy, bundle together the most common packages, including
+\texttt{scikit-image}.
 
@@
 ratio. Several denoising filters are available for image restoration,
-from general-purpose filters such as median and bilateral filters, to more
-specific filters. Total-variation denoising \citep{Chambolle2004,
-Getreuer2012} is well-suited to restore
-piecewise-constant images, such as images with a small number of phases
-encountered in materials science \citep{Bouttes2015}. Conversely, images
-with a fine-grained texture are better preserved with non-local means
-denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
+from general-purpose filters such as median and bilateral filters, to
+more specific filters. Total-variation denoising \citep{Chambolle2004,
+Getreuer2012} is well-suited to restore piecewise-constant images (see
+Fig.~\ref{fig:tomo_gallery}), such as images with a small number of
+phases encountered in materials science \citep{Bouttes2015}. Conversely,
+images with a fine-grained texture are better preserved with non-local
+means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
 
@@
 
-\emma{Juan or Stéfan, can you add something about dask?}
+An easy solution consists in dividing an image into smaller images (with
+or without overlap, depending on the operation), and to apply the
+same operation on the different sub-images, on different cores.
+Creating overlapping chunks is easy with the dedicated function \texttt{view\_as\_windows} (or \texttt{view\_as\_blocks} for contiguous non-overlapping chunks):
+\begin{lstlisting}[language=Python]
+>>> from skimage import util, data
+>>> im = data.camera()
+>>> im.shape
+(512, 512)
+>>> # chunks of size 120 with 8-pixel overlap
+>>> chunks = util.view_as_windows(im, (128, 128), step=120)
+>>> chunks.shape
+(4, 4, 128, 128)
+\end{lstlisting}
+The \texttt{joblib} module enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:  
+\begin{lstlisting}
+>>> from joblib import Parallel, delayed
+>>> filtered_chunks = Parallel(n_jobs=4)(delayed(filters.gaussian)(chunks[i, j]) for i in range(4) for j in range(4))
+\end{lstlisting}
+\texttt{scikit-image} also offers experimental support for a more integrated parallel processing pipeline, thanks to the \texttt{dask} \citep{dask} module:
+\begin{lstlisting}
+filtered_im = util.apply_parallel(filters.gaussian, im, depth=8)
+\end{lstlisting}
+The size of chunks is determined automatically from the number of available cpus, or can be specified by the user.
 
-Prototyping the image processing workflow requires several trial and error
+On a different note, prototyping the image processing workflow requires several trial and error
 executions of scripts containing different operations. The \texttt{joblib}
@@
 
-The success of a software package aimed at end-users is strongly
-correlated to the quality of its documentation (find citation).
+The quality of software documentation is an important component to the
+success of a package aimed at scientists.
 \texttt{scikit-image} users have access to different kinds of
-documentation. Functions of the API (define API here or above) are all
+documentation. Functions of the API are all
 documented using the same standard \citep{Pawlik2015} as other major
@@
 In addition, a popular documentation tool is the graphical gallery of
-examples (\url{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
+examples (\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
 The principle of the gallery is to accelerate the learning curve of image
@@
 include an example for the gallery.
-
 Longer tutorials and a more narrative documentation is available as well
-in the User Guide of \texttt{scikit-image}. The User Guide explains in
-particular...
+in the online User Guide of \texttt{scikit-image}. The User Guide explains in
+particular "big picture" aspects of \texttt{scikit-image}, such as its
+use of \texttt{NumPy} arrays as images, or how the package interacts with
+other parts of the scientific Python ecosystem.
 
@@
 overestimate the number of active users, all the more if the package is
-bundled with others in a software distribution, like Anaconda or Canopy.
-A view closer to reality can be obtained by analyzing the statistics of
-visits of the online help, available on the project website.  As of the
-first half of 2016, 20000 unique visitors per month visit the website of
-scikit-image \url{http://scikit-image.org/}. These users come from 80
-countries, located almost equally in Europe, America and Asia (Oceania
-and Africa representing a much smaller fraction of visitors).
+bundled with others in a software distribution, like Anaconda or
+Canopy. A view closer to reality can be obtained by analyzing the
+statistics of visits of the online help, available on the project
+website.  As of the first half of 2016, 20000 unique visitors visit the
+website of scikit-image every month \url{http://scikit-image.org/}. These
+users come from 80 countries, located almost equally in Europe, America
+and Asia (Oceania and Africa representing a much smaller fraction of
+visitors).
 
@@
 ensures that new features are proposed to users on a regular basis.
+
+\section*{Challenges and roadmap}
 

### 2016-08-19 skimage_tomo.tex
Wrote conclusion section

@@
 
-\section*{Challenges and roadmap}
+\section*{Conclusion}
 
-\section*{Conclusion}
+\texttt{scikit-image} offers a wide variety of image processing
+algorithms, using a simple interface natively compatible with 2D and 3D
+images. It is well integrated into the Scientific Python ecosystem, so
+that it interfaces well with visualization libraries or other data
+processing packages. \texttt{scikit-image} has seen a tremendous growth
+since its creation in 2010, both in terms of users and proposed features.
+In addition to the growing number of scientific teams that use
+\texttt{scikit-image} for processing X-ray-modalities images,
+domain-specific tools are now using \texttt{scikit-image} as a dependency
+to build upon. Examples include \texttt{tomopy} \citep{Gursoy2014} for
+tomographic reconstruction, or \texttt{DIOPTAS} \citep{Prescher2015} for
+the reduction and exploration of X-ray diffraction data. It is likely
+that more application-specific softwares will benefit from depending on
+\texttt{scikit-image} in the future, since \texttt{scikit-image} strives
+to be domain-agnostic and to keep a stable interface. On the end-user
+side, future work includes a better integration of parallel processing
+capabilities, completion of full 3-D compatibility, an enriched narrative
+documentation, and the extension of the number of algorithms.
 
@@
 \section*{Competing interests}
-: The authors declare that the research was conducted
+The authors declare that the research was conducted
 in the absence of any commercial or financial relationships that could be

### 2016-08-20 skimage_tomo.tex
Completed Fig. 3 thanks to Juan's example.

@@
 	public domain), blob detection using the
-	Laplacian of Gaussian method. Bottom: ??
+	Laplacian of Gaussian method. Bottom: ridge detection using the
+	leading value of the Hessian matrix. 
 	\textbf{Segmentation - } Top: super-pixel segmentation
@@
 
-\emma{Insert paragraph on features detection here? Juan?} Diffraction
-peaks in 2D diffraction images can be extracted using blob detection
-methods \citep{Ashiotis2015}, such as the Laplacian of Gaussian method
-(see Fig.~\ref{fig:tomo_gallery}).
+\texttt{scikit-image} offers a wide variety of functions to detect
+geometrical features of interest in an image. Diffraction peaks in 2D
+diffraction images can be extracted using blob detection methods
+\citep{Ashiotis2015}, such as the Laplacian of Gaussian method (see
+Fig.~\ref{fig:tomo_gallery}). In order to detect thin boundaries, the
+ridges of an image can be accessed as regions of high leading eigenvalue
+of the local Hessian matrix (see Fig.~\ref{fig:tomo_gallery}).
 

### 2016-08-20 skimage_tomo.tex
Update abstract/intro

@@
     The exploration and processing of images is a vital aspect of the
-    scientific workflow of different X-ray imaging modalities. Users
-    require tools combining interactivity, versatility, and performance.
+    scientific workflows of many X-ray imaging modalities. Users
+    require tools that combine interactivity, versatility, and performance.
 
     \texttt{scikit-image} is an open-source image processing toolkit for
-    the Python language, that supports a large variety of file formats
+    the Python language that supports a large variety of file formats
     and is compatible with 2-D and 3-D images. The toolkit exposes a
-    simple programming interface, corresponding to functions performing
-    operations on images, and different thematic modules that group these
-    functions according to their purpose, such as image restoration,
+    simple programming interface for functions that perform various
+    operations on images, grouped thematically according to their
+    purpose, e.g. image restoration,
     segmentation, measurements, etc. \texttt{scikit-image} users benefit
-    from the rich ecosystem of Python for science, with powerful
-    visualization libraries or machine learning toolkits.
-    \texttt{scikit-image} combines a gentle
+    from a rich scientific Python ecosystem that contains many
+    powerful libraries for tasks such as visualization or machine learning.
+    \texttt{scikit-image} provides a gentle
     learning curve, versatile image processing capabilities, and the
@@
 programming language gives finer control and more possibilities, provided
-classical processing algorithms can be called from libraries -- hence
-limiting the programming task and the risk of bugs. Matlab (TM) and its
+classical processing algorithms can be called from libraries -- thereby
+limiting the complexity of the programming task and the risk of bugs. Matlab (TM) and its
 image processing toolbox are popular in the academic community of

### 2016-08-20 skimage_tomo.tex
Add suggestions for overview section

--- 2016-08-20 skimage_tomo.tex
@@
 In this section, we provide a short overview of the typical use patterns of
-\texttt{scikit-image}, illutrated by short snippets of code. Indeed, since
+\texttt{scikit-image}, illutrated by short snippets of code. Since
 Python is a programming language, the user interacts with data objects and
-images through code, which is either typed and executed in an interactive
-interpreter, or written in text files (scripts) that are executed.
+images through code, which is either entered and executed in an interactive
+interpreter, or written in text files (so-called scripts) that are executed.
 
@@
 
-Images are manipulated as numerical arrays of uniform
-data type, a format that guarantees a fast access to the computer memory. The
-n-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
+Images are manipulated as numerical arrays, each with a single, uniform
+data type.  This common format guarantees interoperability with other
+libraries and straightforward access to and interpretation of computer memory. The
+N-dimensional (2-D, 3-D, \dots) numerical array object is provided by the
 \texttt{NumPy} module \citep{Vanderwalt2011}.
 
-In image processing, one of the first tasks is therefore to generate
-\texttt{NumPy} arrays, which is often done by reading data from files. We
-read one 2-D image from a file and display it with the following lines of code:
+In image processing in Python, one of the first tasks then is to generate
+\texttt{NumPy} arrays, which is often achieved by reading data from files. We
+read one 2-dimensional image from a file and display it as follows:
 
@@
 \texttt{skimage} is the name under which \texttt{scikit-image} is imported in
-Python code. Note that functions (such as \texttt{imread} to read an image
-file, or \texttt{imshow} to display an image) are found in thematic submodules of
+Python code. Note that functions (such as \texttt{imread} that reads an image
+file, or \texttt{imshow} that displays an image) are found in thematic submodules of
 \texttt{skimage}, such as \texttt{io} for Input/Output.
@@
 \lstinputlisting[language=Python]{io_coll.py}
-Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are opened using modules such as \texttt{h5py} or \texttt{pytables}.
+Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
 
 \texttt{scikit-image} has a very simple Application Programming Interface
-(API), based almost only on
+(API), based almost exclusively on
 functions. Most functions take an image (\emph{i.e} a multi-dimensional
@@
 
-Optional parameters can be passed as Python's \emph{keyword arguments},
+Optional parameters can be passed as Python \emph{keyword arguments},
 in addition to the image parameter.
@@
 \end{lstlisting}
-Therefore, the image processing workflow can be considered as a directed graph
+Therefore, the image processing workflow can be seen as a directed graph
 (a richer structure than a linear pipeline), where nodes are image-shaped arrays, and
@@
 
-Most functions take indifferently 2-D or 3-D images as arguments, so that
+Most functions take both 2-D and 3-D images as arguments, so that
 the same functions can be used to process tomography and microscopy
-images. Only a few functions do not support 3-D images and raise an error
+images. The rest raise an error
 when passed a 3-D argument:
@@
 
-Another type of functions returns numerical value(s) that do not
-correspond to image objects, such as pixel coordinates of objects of
+While the majority of functions return processed images, returns can
+also be numerical value(s) such as pixel coordinates of objects of
 interest or statistical

### 2016-08-20 skimage_tomo.tex
Suggestions for ecosystem / interpreter sections

--- 2016-08-20 skimage_tomo.tex
@@
 from the features of the package alone, but also from the rich
-environment of Scientific Python \citep{Oliphant2007, Perez2011}.
+environment surrounding scientific Python \citep{Oliphant2007, Perez2011}.
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
@@
 
-While several interpreters are available to execute interactively Python
-instructions and scripts, the most popular one in the scientific world is
-the IPython interpreter \citep{Perez2007, Rossant2015}. IPython is an
+While several interpreters are available to execute Python
+instructions and scripts interactively, the most popular in the scientific world is
+IPython \citep{Perez2007, Rossant2015}. IPython is an
 advanced interpreter, which integrates syntax highlighting, text auto-completion,
@@
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
-from the IPython project. Jupyter notebooks provide an interactive development
+out of the IPython project. Jupyter notebooks provide an interactive development
 environment within a web browser, where live code can be enriched
@@
 Cropping or downsampling an image, or retrieving pixels corresponding to
-a given label in a segmentation are all one-liners NumPy code. To
-illustrate the compactness of NumPy code, modifying pixels values below a
-threshold can be written as
+a given label in a segmentation are all NumPy ``one-liners''. To
+illustrate the compactness of NumPy code, consider modifying pixel values below a
+threshold.  This operation can be written as
 \begin{lstlisting}
@@
 \end{lstlisting}
-using the possibility to index arrays with boolean arrays, called
+exploiting the possibility of indexing arrays with boolean arrays, also called
 \emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
@@
 For example, cropping a subvolume as follows does not create a copy of the
-original array:
+original array
 \begin{lstlisting}
@@
 \end{lstlisting}
+but instead refers to the correct memory offsets in the original.
 

### 2016-08-20 skimage_tomo.tex
Add suggestions for visualization / advanced library sections

@@
 from the features of the package alone, but also from the rich
-environment surrounding scientific Python \citep{Oliphant2007, Perez2011}.
+environment of Scientific Python \citep{Oliphant2007, Perez2011}.
 Fig.~\ref{fig:ecosystem} illustrates how several components of this
@@
 
-While several interpreters are available to execute Python
-instructions and scripts interactively, the most popular in the scientific world is
-IPython \citep{Perez2007, Rossant2015}. IPython is an
+While several interpreters are available to execute interactively Python
+instructions and scripts, the most popular one in the scientific world is
+the IPython interpreter \citep{Perez2007, Rossant2015}. IPython is an
 advanced interpreter, which integrates syntax highlighting, text auto-completion,
@@
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
-out of the IPython project. Jupyter notebooks provide an interactive development
+from the IPython project. Jupyter notebooks provide an interactive development
 environment within a web browser, where live code can be enriched
@@
 Cropping or downsampling an image, or retrieving pixels corresponding to
-a given label in a segmentation are all NumPy ``one-liners''. To
-illustrate the compactness of NumPy code, consider modifying pixel values below a
-threshold.  This operation can be written as
+a given label in a segmentation are all one-liners NumPy code. To
+illustrate the compactness of NumPy code, modifying pixels values below a
+threshold can be written as
 \begin{lstlisting}
@@
 \end{lstlisting}
-exploiting the possibility of indexing arrays with boolean arrays, also called
+using the possibility to index arrays with boolean arrays, called
 \emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
@@
 For example, cropping a subvolume as follows does not create a copy of the
-original array
+original array:
 \begin{lstlisting}
@@
 \end{lstlisting}
-but instead refers to the correct memory offsets in the original.
 
@@
 Visualizing images is an important component of the image processing
-workflow, in order to verify the final result and to adjust the
+workflow, used to inspect the final result and to adjust the
 parameters of intermediate processing operations.
@@
 visualizations, a large majority of VTK capabilities can be accessed
-thanks to a pipeline API.
+through mayavi's pipeline API.
 \texttt{mayavi} offers a good trade-off between simplicity of use for
-common operations, and more advanced possibilities, including responsive
+common operations, and accessibility to more sophisticated
+capabilities such as responsive
 visualizations.
@@
 \texttt{scikit-learn} \citep{Pedregosa2011}, a Python module for machine
-learning using \texttt{NumPy} arrays. If local features of an image
+learning using \texttt{NumPy} arrays. Local features of an image
 (such as local statistics of gray levels, or geometric points of
-interest), or features of segmented objects (e.g. geometrical and
-intensity characteristics of segmented particles) are extracted with
-functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}), it
-is then possible to use a \emph{classification} algorithm of
-\texttt{scikit-learn}, either for labeling pixels (a segmentation task)
+interest) or features of segmented objects (e.g. geometrical and
+intensity characteristics of segmented particles) can be extracted with
+functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}). It
+is then possible to use a \emph{classification} algorithm from
+\texttt{scikit-learn} to label pixels (a segmentation task)
 or to classify whole images or objects that have already been segmented.

### 2016-08-21 skimage_tomo.tex
Add suggestions for section Image Processing Capabilities

@@
 Visualizing images is an important component of the image processing
-workflow, used to inspect the final result and to adjust the
+workflow, in order to verify the final result and to adjust the
 parameters of intermediate processing operations.
@@
 visualizations, a large majority of VTK capabilities can be accessed
-through mayavi's pipeline API.
+thanks to a pipeline API.
 \texttt{mayavi} offers a good trade-off between simplicity of use for
-common operations, and accessibility to more sophisticated
-capabilities such as responsive
+common operations, and more advanced possibilities, including responsive
 visualizations.
@@
 \texttt{scikit-learn} \citep{Pedregosa2011}, a Python module for machine
-learning using \texttt{NumPy} arrays. Local features of an image
+learning using \texttt{NumPy} arrays. If local features of an image
 (such as local statistics of gray levels, or geometric points of
-interest) or features of segmented objects (e.g. geometrical and
-intensity characteristics of segmented particles) can be extracted with
-functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}). It
-is then possible to use a \emph{classification} algorithm from
-\texttt{scikit-learn} to label pixels (a segmentation task)
+interest), or features of segmented objects (e.g. geometrical and
+intensity characteristics of segmented particles) are extracted with
+functions from \texttt{skimage.feature} (see Fig.~\ref{fig:ecosystem}), it
+is then possible to use a \emph{classification} algorithm of
+\texttt{scikit-learn}, either for labeling pixels (a segmentation task)
 or to classify whole images or objects that have already been segmented.
@@
 
-\texttt{scikit-image} offers all the classical operations of image
-processing, such as exposure and color adjustment, filtering,
-segmentation, features extraction, geometric transformations or
-measurements of region characteristics. For these
-different categories, the package includes both standard generic
-operations and more advanced algorithms. A sample of
-\texttt{scikit-image} capabilities is given in
+\texttt{scikit-image} offers most classical image processing operations,
+such as exposure and color adjustment, filtering,
+segmentation, feature extraction, geometric transformations, and
+measurements of region characteristics. In addition, some advanced
+algorithms are also implemented, a selection of which is illustrated in
 Fig.~\ref{fig:tomo_gallery}.
@@
 Tomographic images often suffer from artifacts or poor signal-to-noise
-ratio. Several denoising filters are available for image restoration,
-from general-purpose filters such as median and bilateral filters, to
-more specific filters. Total-variation denoising \citep{Chambolle2004,
-Getreuer2012} is well-suited to restore piecewise-constant images (see
+ratio. Several denoising filters are available for restoring these
+images, ranging from general-purpose median and bilateral
+filters to those more suited to specific applications. For example, total-variation denoising \citep{Chambolle2004,
+Getreuer2012} is ideal for restoring piecewise-constant images (see
 Fig.~\ref{fig:tomo_gallery}), such as images with a small number of
@@
 
-\texttt{scikit-image} offers a wide variety of functions to detect
-geometrical features of interest in an image. Diffraction peaks in 2D
+\texttt{scikit-image} offers a wide variety of functions for detecting
+geometrical features of interest in an image. Peaks in 2D
 diffraction images can be extracted using blob detection methods
@@
 Fig.~\ref{fig:tomo_gallery}). In order to detect thin boundaries, the
-ridges of an image can be accessed as regions of high leading eigenvalue
-of the local Hessian matrix (see Fig.~\ref{fig:tomo_gallery}).
+ridges of an image can be identified as regions for which the leading eigenvalue
+of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery}).
 
-Segmentation of regions of interest can be achieved using different
+Segmentation of regions of interest can be achieved using one of various
 strategies, depending on the characteristics of the image. Images with a
@@
 several thresholding algorithms, including an adaptive local thresholding
-algorithm aimed at images with contrast variations. Super-pixel
+algorithm aimed at images with strong contrast variations. Super-pixel
 algorithms \citep{Felzenszwalb2004, Achanta2012} (see
 Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
-super-pixels, by grouping pixels that are close together both in color-
-and direct space. Region-growing algorithms, such as the morphological
+super-pixels, by grouping pixels that are close together both in color
+and spatial distance. Region-growing algorithms, such as the morphological
 watershed or the random walker \citep{Grady2006}, propagate the labels

### 2016-08-21 skimage_tomo.tex
Various text tweaks

--- 2016-08-20 skimage_tomo.tex
@@
     and is compatible with 2-D and 3-D images. The toolkit exposes a
-    simple programming interface, corresponding to functions performing
-    operations on images, and different thematic modules that group these
+    simple programming interface, with thematic modules grouping
     functions according to their purpose, such as image restoration,
-    segmentation, measurements, etc. \texttt{scikit-image} users benefit
+    segmentation, and measurements. \texttt{scikit-image} users benefit
     from the rich ecosystem of Python for science, with powerful
@@
 
-\texttt{scikit-image} has a very simple Application Programming Interface
+\texttt{scikit-image} has a simple Application Programming Interface
 (API), based almost only on
@@
 	\texttt{scikit-image}.} From left to right and top to bottom.
-	Data are syntheric, unless stated otherwise.
+	Data are synthetic, unless stated otherwise.
 	\textbf{Filtering -} Top: non-local means denoising of an image
@@
 \end{lstlisting}
-The \texttt{joblib} module enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:  
+The \texttt{joblib} library enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:
 \begin{lstlisting}

### 2016-08-21 skimage_tomo.tex
Suggested updates for last section

@@
     and is compatible with 2-D and 3-D images. The toolkit exposes a
-    simple programming interface, with thematic modules grouping
+    simple programming interface, corresponding to functions performing
+    operations on images, and different thematic modules that group these
     functions according to their purpose, such as image restoration,
-    segmentation, and measurements. \texttt{scikit-image} users benefit
+    segmentation, measurements, etc. \texttt{scikit-image} users benefit
     from the rich ecosystem of Python for science, with powerful
@@
 
-\texttt{scikit-image} has a simple Application Programming Interface
+\texttt{scikit-image} has a very simple Application Programming Interface
 (API), based almost only on
@@
 	\texttt{scikit-image}.} From left to right and top to bottom.
-	Data are synthetic, unless stated otherwise.
+	Data are syntheric, unless stated otherwise.
 	\textbf{Filtering -} Top: non-local means denoising of an image
@@
 
-Given the large size of tomography datasets, the speed of execution of image
-processing operations is a critical issue. \texttt{scikit-image} relies mostly
-on calls to \texttt{NumPy} operations, with most of them that are performed in
-optimized compiled code (C or Fortran). Performance-critical parts of the code
+Given the large size of tomography datasets, the execution speed of image
+processing operations is of critical concern. \texttt{scikit-image} relies mostly
+on calls to \texttt{NumPy} operations, of which most are performed in
+optimized compiled code (C or Fortran). Performance-critical parts of \texttt{scikit-image}
 that cannot call efficient \texttt{NumPy} code are implemented in
@@
 workstations and servers used for X-ray imaging typically have several tens of
-cores. Parallelization of the computing workflow can be achieved in different
-ways. The most trivial parallelization scheme consists in applying the same
+cores. Parallelization of the computing workflow can be achieved in multiple
+ways. The most trivial parallelization scheme consists of applying the same
 workflow to different images, on different cores. However, finer-grained
@@
 \end{lstlisting}
-The \texttt{joblib} library enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:
+The \texttt{joblib} module enables easy parallel processing. Looping over the different blocks, and dispatching the computation over several cores, is realized with the following syntax:  
 \begin{lstlisting}
@@
 
-On a different note, prototyping the image processing workflow requires several trial and error
-executions of scripts containing different operations. The \texttt{joblib}
+Another situation that often arises is that, while prototyping a
+workflow, scripts (containing the image processing pipeline) are run
+several times to experiment with parameters. The \texttt{joblib}
 module provides a caching mechanism that avoids the repetition of function
-calls, if their arguments have not changed:
+calls if their arguments have not changed:
 \begin{lstlisting}
@@
 >>> filtered_again = median(im, np.ones((3, 3)))
->>> # the above call did not trigger an evaluation
+>>> # the above call did not trigger another evaluation
 \end{lstlisting}
@@
 implementation of a more recent algorithm \citep{Darbon2008} that modifies the
-internal organization of loops, it was possible to gain a factor of 5 to 10.
-The large size of the \texttt{scikit-image} community ensures that possible
-algorithmic improvements are discussed regularly.
+internal organization of loops, it was possible to improve execution
+time by a factor of roughly ten times.
+The large size of the \texttt{scikit-image} community makes it likely for
+algorithmic improvements to be discussed regularly.
 
@@
 
-The quality of software documentation is an important component to the
-success of a package aimed at scientists.
-\texttt{scikit-image} users have access to different kinds of
+The quality of software documentation is (perhaps especially)
+important in software aimed at scientists.
+\texttt{scikit-image} users have access to several kinds of
 documentation. Functions of the API are all
@@
 Scientific Python packages. The standard include a description of all
-input and output variables and their data type, together with
-explanations on what the function does and how to use it. Function
+input and output variables and their data types, together with
+explanations of what each function does and how to use it. Function
 documentation is accessed either online, or within the development
@@
 
-In addition, a popular documentation tool is the graphical gallery of
-examples (\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
-The principle of the gallery is to accelerate the learning curve of image
-processing, by showcasing graphical examples of image processing
-operations. Such examples are organized as an array of thumbnails with a
+In addition, a graphical gallery of examples
+(\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}),
+part of which is displayed in Fig.~\ref{fig:gallery},
+showcases graphical examples of image processing
+operations.  The examples are organized as an array of thumbnails with a
 short title (see Fig.~\ref{fig:gallery} left). These thumbnails link to
@@
 in the online User Guide of \texttt{scikit-image}. The User Guide explains in
-particular "big picture" aspects of \texttt{scikit-image}, such as its
+particular "big picture", foundational aspects of \texttt{scikit-image}, such as its
 use of \texttt{NumPy} arrays as images, or how the package interacts with
@@
 Estimating the number of active users of an open-source package is a
-difficult task. Statistics of downloads, for example, largely
+difficult task. Download statistics, for example, largely
 overestimate the number of active users, all the more if the package is
@@
 statistics of visits of the online help, available on the project
-website.  As of the first half of 2016, 20000 unique visitors visit the
-website of scikit-image every month \url{http://scikit-image.org/}. These
+website.  As of the first half of 2016, 20000 unique visitors visited the
+\texttt{scikit-image} website every month at \url{http://scikit-image.org/}. These
 users come from 80 countries, located almost equally in Europe, America
@@
 \texttt{scikit-image} is developed by a diverse team of volunteers, with
-more than 170 developers that have contributed to the package. The large
+more than 170 developers having contributed to the package. The large
 number of developers and users is a key element of the sustainability of
@@
 \url{https://github.com/scikit-image/scikit-image}, where users and
-developers propose and discuss new contributions, or report bugs or ideas
+developers propose and discuss new contributions, report bugs or submit ideas
 for improvements.
 A release cycle of one or two releases every year
-ensures that new features are proposed to users on a regular basis.
+ensures that new features are propagated to users on a regular basis.
 
@@
 images. It is well integrated into the Scientific Python ecosystem, so
-that it interfaces well with visualization libraries or other data
-processing packages. \texttt{scikit-image} has seen a tremendous growth
-since its creation in 2010, both in terms of users and proposed features.
+that it interfaces well with visualization libraries and other data
+processing packages. \texttt{scikit-image} has seen tremendous growth
+since its creation in 2009, both in terms of users and proposed features.
 In addition to the growing number of scientific teams that use
-\texttt{scikit-image} for processing X-ray-modalities images,
+\texttt{scikit-image} for processing images of various X-ray modalities,
 domain-specific tools are now using \texttt{scikit-image} as a dependency
@@
 the reduction and exploration of X-ray diffraction data. It is likely
-that more application-specific softwares will benefit from depending on
+that more application-specific software will benefit by depending on
 \texttt{scikit-image} in the future, since \texttt{scikit-image} strives
-to be domain-agnostic and to keep a stable interface. On the end-user
-side, future work includes a better integration of parallel processing
+to be domain-agnostic and to keep the function interface stable. On the end-user
+side, future work includes better integration of parallel processing
 capabilities, completion of full 3-D compatibility, an enriched narrative
-documentation, and the extension of the number of algorithms.
+documentation, speed enhancements, and expansion of the set of supported algorithms.
 

### 2016-08-21 skimage_tomo.tex
Further minor edits

--- 2016-08-21 skimage_tomo.tex
@@
 processing packages for macromolecular cristallography \citep{Adams2010},
-azimuthal integration of diffraction data \citep{Ashiotis2015} or
+azimuthal integration of diffraction data \citep{Ashiotis2015}, or
 fluorescence analysis \citep{pymca}.
@@
 	scikit-image functions can be passed to other Python modules
-	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
+	relying on \texttt{NumPy} arrays, such as \texttt{SciPy} or
 	\texttt{scikit-learn}. Image-shaped arrays are transformed into
@@
 
-Most functions take indifferently 2-D or 3-D images as arguments, so that
-the same functions can be used to process tomography and microscopy
-images. Only a few functions do not support 3-D images and raise an error
+Most functions transparently handle 2-D, 3-D, or even higher-dimensional
+images as arguments, so
+the same functions can be used to process tomography, microscopy, or natural
+images. A few functions do not support 3-D images and raise an error
 when passed a 3-D argument:
@@
 
-Another type of functions returns numerical value(s) that do not
-correspond to image objects, such as pixel coordinates of objects of
-interest or statistical
+However, the proportion of functions supporting 3D images is always increasing,
+thanks to the many contributors to the library.
+
+A subset of functions returns not images but other value types,
+such as pixel coordinates of objects of interest, or statistical
 information about the image:
@@
 
-While several interpreters are available to execute interactively Python
+While several interpreters are available to execute Python
 instructions and scripts, the most popular one in the scientific world is
@@
 introspection and profiling methods, and online help. Several
-Integrated Development Environments (IDEs) include IPython,
+Integrated Development Environments (IDEs) come bundled with IPython,
 together with other components such as a text editor. Notable examples
@@
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
-from the IPython project. Jupyter notebooks provide an interactive development
+from the IPython project. Jupyter notebooks provide a development
 environment within a web browser, where live code can be enriched
 by explanatory text, equations and visualizations (FIGURE).
-(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
+As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
+demonstrating their wide adoption by the community as workflow-sharing
+tools (http://archive.ipython.org/media/SciPy2016JupyterLab.pdf).
 
@@
 \end{lstlisting}
-using the possibility to index arrays with boolean arrays, called
-\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
-making new copies of arrays whenever possible, which is a important
+using the ability to index arrays with boolean arrays, called
+\emph{masking}. \texttt{NumPy} uses memory sparingly and avoids
+making new copies of arrays whenever possible, an important
 requirement when dealing with the gigabyte-sized images of tomography.

### 2016-08-21 skimage_tomo.tex
More edits

@@
 demonstrating their wide adoption by the community as workflow-sharing
-tools (http://archive.ipython.org/media/SciPy2016JupyterLab.pdf).
+tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
 
@@
 visualizations, a large majority of VTK capabilities can be accessed
-thanks to a pipeline API.
+through its pipeline API.
 \texttt{mayavi} offers a good trade-off between simplicity of use for
@@
 or to classify whole images or objects that have already been segmented.
-The interoperability between these packages is ensured by the common use
-of \texttt{NumPy} arrays, so that the tasks described above are
-implemented with a few lines of code.
+The near-universal use of \texttt{NumPy} arrays ensures the interoperability
+between these packages, so that just a few lines of code are sufficient
+to create these sophisticated workflows.
 
 The modularity of the Scientific Python ecosystem may be
-confusing at first sight. Nevertheless, core modules of this ecosystem
+confusing at first sight, but the core modules of this ecosystem
 are almost perfectly compatible, thanks to the shared use of NumPy arrays
 and common development practices (although they are developed in parallel
-by different teams). Several integrated distributions, such as Anaconda
-or Canopy, bundle together the most common packages, including
+by different teams). Several ``distributions'', such as Anaconda
+or Canopy, bundle together the most popular libraries, including
 \texttt{scikit-image}.
@@
 	Laplacian of Gaussian method. Bottom: ridge detection using the
-	leading value of the Hessian matrix. 
+	leading eigenvalue of the Hessian matrix.
 	\textbf{Segmentation - } Top: super-pixel segmentation
@@
 algorithm aimed at images with contrast variations. Super-pixel
-algorithms \citep{Felzenszwalb2004, Achanta2012} (see
-Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
+algorithms \citep{Felzenszwalb2004, Achanta2012} create an over-segmentation
+of images in
 super-pixels, by grouping pixels that are close together both in color-
-and direct space. Region-growing algorithms, such as the morphological
+and direct space (see Fig.~\ref{fig:tomo_gallery}). Region-growing
+algorithms, such as the morphological
 watershed or the random walker \citep{Grady2006}, propagate the labels
@@
 
-On a different note, prototyping the image processing workflow requires several trial and error
-executions of scripts containing different operations. The \texttt{joblib}
-module provides a caching mechanism that avoids the repetition of function
+\em{Caching} provides another tool to speed up data analysis. Prototyping an
+image processing workflow often requires several trial and error
+executions of scripts containing different operations. \texttt{joblib}
+provides a caching mechanism that avoids the repetition of function
 calls, if their arguments have not changed:
@@
 
-Finally, let us note that the biggest performance improvements often come from
+Finally, we note that the biggest performance improvements often come from
 the improvement of algorithms (as opposed to computing architectures only). For
@@
 implementation of a more recent algorithm \citep{Darbon2008} that modifies the
-internal organization of loops, it was possible to gain a factor of 5 to 10.
+internal organization of loops, it was possible to gain a 5- to 10-fold speedup.
 The large size of the \texttt{scikit-image} community ensures that possible
@@
 
-The quality of software documentation is an important component to the
-success of a package aimed at scientists.
+The quality of the documentation is an important component to the
+success of a software package.
 \texttt{scikit-image} users have access to different kinds of
-documentation. Functions of the API are all
-documented using the same standard \citep{Pawlik2015} as other major
-Scientific Python packages. The standard include a description of all
+documentation. All functions are
+documented using the NumPy documentation standard \citep{Pawlik2015},
+which is universal across all major
+Scientific Python packages. The standard includes a description of all
 input and output variables and their data type, together with
 explanations on what the function does and how to use it. Function
-documentation is accessed either online, or within the development
-environment (IPython, Spyder, Jupyter Notebook...).
+documentation is accessible online or within the development
+environment itself (IPython, Spyder, Jupyter Notebook...).
 
@@
 \caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
- The gallery of examples consists of an array of thumbnails (left part), which link to example webpages, each centerered on a specific image processing task.
-Each webpage includes Python code generating a figure, the figure itself, as well as a short tutorial explaining the image processing operations and the code.
+ The gallery of examples consists of an array of thumbnails (left), which link to example webpages, each centerered on a specific image processing task.
+Each webpage includes Python code generating a figure, the figure itself, and a short tutorial explaining the image processing operations and the code.
 \label{fig:gallery}}
@@
 In addition, a popular documentation tool is the graphical gallery of
-examples (\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}), a part of which is displayed in Fig.~\ref{fig:gallery}.
+examples (\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}),
+an example of which appears in Fig.~\ref{fig:gallery}.
 The principle of the gallery is to accelerate the learning curve of image
-processing, by showcasing graphical examples of image processing
+processing, by showcasing graphical examples of common image processing
 operations. Such examples are organized as an array of thumbnails with a
@@
 Longer tutorials and a more narrative documentation is available as well
-in the online User Guide of \texttt{scikit-image}. The User Guide explains in
-particular "big picture" aspects of \texttt{scikit-image}, such as its
+in the online User Guide, which explains
+"big picture" aspects of \texttt{scikit-image}, such as its
 use of \texttt{NumPy} arrays as images, or how the package interacts with
@@
 overestimate the number of active users, all the more if the package is
-bundled with others in a software distribution, like Anaconda or
+bundled with others in a software distribution, such as Anaconda or
 Canopy. A view closer to reality can be obtained by analyzing the
@@
 users come from 80 countries, located almost equally in Europe, America
-and Asia (Oceania and Africa representing a much smaller fraction of
+and Asia (with Oceania and Africa representing a much smaller fraction of
 visitors).
@@
 
-\texttt{scikit-image} is developed by a diverse team of volunteers, with
-more than 170 developers that have contributed to the package. The large
+\texttt{scikit-image} is developed by a diverse team of volunteers.
+More than 170 individuals have contributed to the package. The large
 number of developers and users is a key element of the sustainability of
 \texttt{scikit-image}. The
-development process takes place on the GitHub platform
+development process takes place on GitHub
 \url{https://github.com/scikit-image/scikit-image}, where users and
@@
 the reduction and exploration of X-ray diffraction data. It is likely
-that more application-specific softwares will benefit from depending on
+that more application-specific software will benefit from depending on
 \texttt{scikit-image} in the future, since \texttt{scikit-image} strives

### 2016-08-21 skimage_tomo.tex

--- 2016-08-21 skimage_tomo.tex
@@
     The exploration and processing of images is a vital aspect of the
-    scientific workflow of different X-ray imaging modalities. Users
-    require tools combining interactivity, versatility, and performance.
+    scientific workflows of many X-ray imaging modalities. Users
+    require tools that combine interactivity, versatility, and performance.
 
     \texttt{scikit-image} is an open-source image processing toolkit for
-    the Python language, that supports a large variety of file formats
+    the Python language that supports a large variety of file formats
     and is compatible with 2-D and 3-D images. The toolkit exposes a
-    simple programming interface, with thematic modules grouping
-    functions according to their purpose, such as image restoration,
-    segmentation, and measurements. \texttt{scikit-image} users benefit
-    from the rich ecosystem of Python for science, with powerful
-    visualization libraries or machine learning toolkits.
-    \texttt{scikit-image} combines a gentle
+    simple programming interface for functions that perform various
+    operations on images, grouped thematically according to their
+    purpose, e.g. image restoration,
+    segmentation, measurements, etc. \texttt{scikit-image} users benefit
+    from a rich scientific Python ecosystem that contains many
+    powerful libraries for tasks such as visualization or machine learning.
+    \texttt{scikit-image} provides a gentle
     learning curve, versatile image processing capabilities, and the
@@
 processing packages for macromolecular cristallography \citep{Adams2010},
-azimuthal integration of diffraction data \citep{Ashiotis2015}, or
+azimuthal integration of diffraction data \citep{Ashiotis2015} or
 fluorescence analysis \citep{pymca}.
@@
 	scikit-image functions can be passed to other Python modules
-	relying on \texttt{NumPy} arrays, such as \texttt{SciPy} or
+	relying on \texttt{NumPy} arrays, such as \texttt{Scipy} or
 	\texttt{scikit-learn}. Image-shaped arrays are transformed into
@@
 \lstinputlisting[language=Python]{io_coll.py}
-Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are opened using modules such as \texttt{h5py} or \texttt{pytables}.
+Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
 
-\texttt{scikit-image} has a simple Application Programming Interface
-(API), based almost only on
+\texttt{scikit-image} has a very simple Application Programming Interface
+(API), based almost exclusively on
 functions. Most functions take an image (\emph{i.e} a multi-dimensional
@@
 
-Most functions transparently handle 2-D, 3-D, or even higher-dimensional
-images as arguments, so
-the same functions can be used to process tomography, microscopy, or natural
-images. A few functions do not support 3-D images and raise an error
+Most functions take both 2-D and 3-D images as arguments, so that
+the same functions can be used to process tomography and microscopy
+images. The rest raise an error
 when passed a 3-D argument:
@@
 
-However, the proportion of functions supporting 3D images is always increasing,
-thanks to the many contributors to the library.
-
-A subset of functions returns not images but other value types,
-such as pixel coordinates of objects of interest, or statistical
+While the majority of functions return processed images, returns can
+also be numerical value(s) such as pixel coordinates of objects of
+interest or statistical
 information about the image:
@@
 
-While several interpreters are available to execute Python
+While several interpreters are available to execute interactively Python
 instructions and scripts, the most popular one in the scientific world is
@@
 introspection and profiling methods, and online help. Several
-Integrated Development Environments (IDEs) come bundled with IPython,
+Integrated Development Environments (IDEs) include IPython,
 together with other components such as a text editor. Notable examples
@@
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
-from the IPython project. Jupyter notebooks provide a development
+from the IPython project. Jupyter notebooks provide an interactive development
 environment within a web browser, where live code can be enriched
 by explanatory text, equations and visualizations (FIGURE).
-As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
-demonstrating their wide adoption by the community as workflow-sharing
-tools (http://archive.ipython.org/media/SciPy2016JupyterLab.pdf).
+(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
 
@@
 \end{lstlisting}
-using the ability to index arrays with boolean arrays, called
-\emph{masking}. \texttt{NumPy} uses memory sparingly and avoids
-making new copies of arrays whenever possible, an important
+using the possibility to index arrays with boolean arrays, called
+\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
+making new copies of arrays whenever possible, which is a important
 requirement when dealing with the gigabyte-sized images of tomography.

### 2016-08-21 skimage_tomo.tex

@@
     \texttt{scikit-image} is an open-source image processing toolkit for
-    the Python language that supports a large variety of file formats
-    and is compatible with 2-D and 3-D images. The toolkit exposes a
-    simple programming interface for functions that perform various
-    operations on images, grouped thematically according to their
-    purpose, e.g. image restoration,
-    segmentation, measurements, etc. \texttt{scikit-image} users benefit
-    from a rich scientific Python ecosystem that contains many
-    powerful libraries for tasks such as visualization or machine learning.
-    \texttt{scikit-image} provides a gentle
-    learning curve, versatile image processing capabilities, and the
-    scalable performances required for the high-throughput analysis of
-    X-ray imaging data.
+    the Python language that supports a large variety of file formats and
+    is compatible with 2-D and 3-D images. The toolkit exposes a simple
+    programming interface, with thematic modules grouping functions
+    according to their purpose, such as image restoration, segmentation,
+    and measurements. \texttt{scikit-image} users benefit from a rich
+    scientific Python ecosystem that contains many powerful libraries for
+    tasks such as visualization or machine learning.
+    \texttt{scikit-image} combines a gentle learning curve, versatile
+    image processing capabilities, and the scalable performances required
+    for the high-throughput analysis of X-ray imaging data.
 
@@
 
-\texttt{scikit-image} has a very simple Application Programming Interface
+\texttt{scikit-image} has a simple Application Programming Interface
 (API), based almost exclusively on
@@
 
-Most functions take both 2-D and 3-D images as arguments, so that
-the same functions can be used to process tomography and microscopy
-images. The rest raise an error
-when passed a 3-D argument:
+Most functions transparently handle 2-D, 3-D, or even higher-dimensional
+images as arguments, so
+the same functions can be used to process tomography, microscopy, or natural
+images. The rest raise an error when passed a 3-D argument:
 \begin{lstlisting}
@@
 \end{lstlisting}
+However, the proportion of functions supporting 3D images is always increasing,
+thanks to the many contributors to the library.
 
@@
 also be numerical value(s) such as pixel coordinates of objects of
-interest or statistical
-information about the image:
+interest or statistical information about the image:
 \begin{lstlisting}
@@
 
-While several interpreters are available to execute Python
-instructions and scripts interactively, the most popular in the scientific world is
-IPython \citep{Perez2007, Rossant2015}. IPython is an
-advanced interpreter, which integrates syntax highlighting, text auto-completion,
-a debugger,
-introspection and profiling methods, and online help. Several
-Integrated Development Environments (IDEs) include IPython,
+While several interpreters are available to execute Python instructions
+and scripts interactively, the most popular in the scientific world is
+IPython \citep{Perez2007, Rossant2015}. IPython is an advanced
+interpreter, which integrates syntax highlighting, text auto-completion,
+a debugger, introspection and profiling methods, and online help. Several
+Integrated Development Environments (IDEs) come bundled with IPython,
 together with other components such as a text editor. Notable examples
@@
 by explanatory text, equations and visualizations (FIGURE).
-(jni: FURTHER TEXT ABOUT IMPACT OF JUPYTER NOTEBOOKS)
+As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
+demonstrating their wide adoption by the community as workflow-sharing
+tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
 
@@
 \end{lstlisting}
-exploiting the possibility of indexing arrays with boolean arrays, also called
-\emph{masking}. Also, \texttt{NumPy} uses memory sparingly and avoids
-making new copies of arrays whenever possible, which is a important
+exploiting the ability to index arrays with boolean arrays, also called
+\emph{masking}. \texttt{NumPy} uses memory sparingly and avoids
+making new copies of arrays whenever possible, an important
 requirement when dealing with the gigabyte-sized images of tomography.
@@
 several thresholding algorithms, including an adaptive local thresholding
-algorithm aimed at images with strong contrast variations. Super-pixel
-algorithms \citep{Felzenszwalb2004, Achanta2012} (see
-Fig.~\ref{fig:tomo_gallery}) create an over-segmentation of images in
-super-pixels, by grouping pixels that are close together both in color
-and spatial distance. Region-growing algorithms, such as the morphological
-watershed or the random walker \citep{Grady2006}, propagate the labels
-of user-defined markers through the image (see
-Fig.~\ref{fig:tomo_gallery}). The active contour
-algorithm \citep{Kass1988} fits snake contours to features of the
-image, such as edges or high-brightness regions.
+algorithm aimed at images with contrast variations. Super-pixel
+algorithms \citep{Felzenszwalb2004, Achanta2012} create an
+over-segmentation of images in super-pixels, by grouping pixels that are
+close together both in color- and spatial distance (see
+Fig.~\ref{fig:tomo_gallery}). Region-growing algorithms, such as the
+morphological watershed or the random walker \citep{Grady2006}, propagate
+the labels of user-defined markers through the image (see
+Fig.~\ref{fig:tomo_gallery}). The active contour algorithm
+\citep{Kass1988} fits snake contours to features of the image, such as
+edges or high-brightness regions.
 
@@
 
-Another situation that often arises is that, while prototyping a
-workflow, scripts (containing the image processing pipeline) are run
-several times to experiment with parameters. The \texttt{joblib}
-module provides a caching mechanism that avoids the repetition of function
-calls if their arguments have not changed:
+\em{Caching} provides another tool to speed up data analysis. A situation
+that often arises is that, while prototyping a workflow, scripts
+(containing the image processing pipeline) are run several times to
+experiment with parameters. \texttt{joblib} provides a caching mechanism
+that avoids the repetition of function calls, if their arguments have not
+changed:
 \begin{lstlisting}
@@
 
-The quality of software documentation is (perhaps especially)
-important in software aimed at scientists.
-\texttt{scikit-image} users have access to several kinds of
-documentation. Functions of the API are all
-documented using the same standard \citep{Pawlik2015} as other major
-Scientific Python packages. The standard include a description of all
-input and output variables and their data types, together with
-explanations of what each function does and how to use it. Function
-documentation is accessed either online, or within the development
-environment (IPython, Spyder, Jupyter Notebook...).
+The quality of software documentation is (perhaps especially) important
+in software aimed at scientists. \texttt{scikit-image} users have access
+to several kinds of documentation. All functions are documented using the
+NumPy documentation standard \citep{Pawlik2015}, which is universal
+across all major Scientific Python packages. The standard include a
+description of all input and output variables and their data types,
+together with explanations of what each function does and how to use it.
+Function documentation is accessible online or within the development
+environment itself (IPython, Spyder, Jupyter Notebook...).
 
@@
 In addition, a graphical gallery of examples
-(\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}),
-part of which is displayed in Fig.~\ref{fig:gallery},
-showcases graphical examples of image processing
-operations.  The examples are organized as an array of thumbnails with a
-short title (see Fig.~\ref{fig:gallery} left). These thumbnails link to
-the webpage of the corresponding example, which features a mini-tutorial
-on the image processing method, the code needed to run the example and
-the figure generated by the example. Since the graphical gallery is an
-efficient way to inform users about the features of
-\texttt{scikit-image}, every new feature integrated in the package must
-include an example for the gallery.
-Longer tutorials and a more narrative documentation is available as well
-in the online User Guide of \texttt{scikit-image}. The User Guide explains in
-particular "big picture", foundational aspects of \texttt{scikit-image}, such as its
-use of \texttt{NumPy} arrays as images, or how the package interacts with
-other parts of the scientific Python ecosystem.
+(\nolinkurl{http://scikit-image.org/docs/dev/auto_examples/}), part of
+which is displayed in Fig.~\ref{fig:gallery}, showcases graphical
+examples of common image processing operations.  The examples are
+organized as an array of thumbnails with a short title (see
+Fig.~\ref{fig:gallery} left). These thumbnails link to the webpage of the
+corresponding example, which features a mini-tutorial on the image
+processing method, the code needed to run the example and the figure
+generated by the example. Since the graphical gallery is an efficient way
+to inform users about the features of \texttt{scikit-image}, every new
+feature integrated in the package must include an example for the
+gallery. Longer tutorials and a more narrative documentation is available
+as well in the online User Guide of \texttt{scikit-image}. The User Guide
+explains in particular "big picture", foundational aspects of
+\texttt{scikit-image}, such as its use of \texttt{NumPy} arrays as
+images, or how the package interacts with other parts of the scientific
+Python ecosystem.
 
@@
 
-\texttt{scikit-image} is developed by a diverse team of volunteers, with
-more than 170 developers having contributed to the package. The large
+\texttt{scikit-image} is developed by a diverse team of volunteers.
+More than 170 individuals have contributed to the package. The large
 number of developers and users is a key element of the sustainability of
 \texttt{scikit-image}. The
-development process takes place on the GitHub platform
+development process takes place on GitHub
 \url{https://github.com/scikit-image/scikit-image}, where users and
@@
 the reduction and exploration of X-ray diffraction data. It is likely
-that more application-specific software will benefit by depending on
+that more application-specific software will benefit from depending on
 \texttt{scikit-image} in the future, since \texttt{scikit-image} strives

### 2016-08-21 skimage_tomo.tex
Moved numpy paragraph before interpreter paragraph in ecosystem section

@@
 images has not decreased as much, so that the outcome of a successful
-synchrotron imaging campaign often takes weeks or even months to be
+synchrotron imaging run often takes weeks or even months to be
 transformed into scientific results.
@@
 
+\paragraph{NumPy arrays} are the cornerstone of the Scientific Python
+ecosystem, and of \texttt{scikit-image} operations in particular.
+Cropping or downsampling an image, or retrieving pixels corresponding to
+a given label in a segmentation are all NumPy ``one-liners''. To
+illustrate the compactness of NumPy code, consider modifying pixel values below a
+threshold.  This operation can be written as
+\begin{lstlisting}
+im[im < 0.5] = 0
+\end{lstlisting}
+exploiting the ability to index arrays with boolean arrays, also called
+\emph{masking}. \texttt{NumPy} uses memory sparingly and avoids
+making new copies of arrays whenever possible, an important
+requirement when dealing with the gigabyte-sized images of tomography.
+For example, cropping a subvolume as follows does not create a copy of the
+original array
+\begin{lstlisting}
+sub_volume = im[100:-100, 100:-100, 100:-100]
+\end{lstlisting}
+but instead refers to the correct memory offsets in the original.
+
 \paragraph{Interpreter and development environment.}
@@
 tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
-
-\paragraph{NumPy arrays} are the cornerstone of the Scientific Python
-ecosystem, and of \texttt{scikit-image} operations in particular.
-Cropping or downsampling an image, or retrieving pixels corresponding to
-a given label in a segmentation are all NumPy ``one-liners''. To
-illustrate the compactness of NumPy code, consider modifying pixel values below a
-threshold.  This operation can be written as
-\begin{lstlisting}
-im[im < 0.5] = 0
-\end{lstlisting}
-exploiting the ability to index arrays with boolean arrays, also called
-\emph{masking}. \texttt{NumPy} uses memory sparingly and avoids
-making new copies of arrays whenever possible, an important
-requirement when dealing with the gigabyte-sized images of tomography.
-For example, cropping a subvolume as follows does not create a copy of the
-original array
-\begin{lstlisting}
-sub_volume = im[100:-100, 100:-100, 100:-100]
-\end{lstlisting}
-but instead refers to the correct memory offsets in the original.
 
@@
 
-\em{Caching} provides another tool to speed up data analysis. A situation
+{\em Caching} provides another tool to speed up data analysis. A situation
 that often arises is that, while prototyping a workflow, scripts

### 2016-08-21 skimage_tomo.tex
Add Jupyter example screenshot and caption

@@
 environment within a web browser, where live code can be enriched
-by explanatory text, equations and visualizations (FIGURE).
+by explanatory text, equations and visualizations (Fig.~\ref{fig:jupyter}).
 As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
@@
 tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
+
+\begin{figure*}
+    \centerline{\includegraphics[width=0.99\textwidth]{jupyter_example}}
+    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
+             plot and text output (middle), and free-form narrative text (bottom).
+             This makes it ideal to record and report code-based analyses.
+             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
+ \label{fig:jupyter}}
+\end{figure*}
 

### 2016-08-21 skimage_tomo.tex
Reference papers that have cited scikit-image

--- 2016-08-21 skimage_tomo.tex
@@
 website.  As of the first half of 2016, 20000 unique visitors visited the
-\texttt{scikit-image} website every month at \url{http://scikit-image.org/}. These
-users come from 80 countries, located almost equally in Europe, America
-and Asia (with Oceania and Africa representing a much smaller fraction of
-visitors).
+\texttt{scikit-image} website every month at
+\url{http://scikit-image.org/}, from 138 countries.
+
+The \texttt{scikit-image} paper of 2014 has been cited by 120 research
+works (as of August 2016, according to Google Scholar), among which
+studies that used X-ray imaging in fields such as medical imaging
+\citep{Shen2015, Malan2016, Blackledge2016}, materials science
+\citep{Bouttes2015} or geoscience \citep{Schluter2014}.
 
@@
 The authors gratefully acknowledge the work of the contributors of
-  \texttt{scikit-image}. E. Gouillart acknowledges the support of ANR
-  project EDDAM ANR-11-BS09-027.
+  \texttt{scikit-image}, and thank S. Deville and D. Vandembroucq for a
+  careful reading of the paper and useful suggestions. E. Gouillart
+  acknowledges the support of ANR project EDDAM ANR-11-BS09-027.
 

### 2016-08-21 skimage_tomo.tex
Labeled panels in Fig. 4 (tomo gallery)

@@
 \begin{figure*}
-    \centerline{\includegraphics[width=0.99\textwidth]{jupyter_example}}
+    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
     \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
@@
     \caption{\csentence{Typical image processing operations with
-	\texttt{scikit-image}.} From left to right and top to bottom.
+	\texttt{scikit-image}.}
 	Data are synthetic, unless stated otherwise.
-	\textbf{Filtering -} Top: non-local means denoising of an image
+	\textbf{a) Filtering -} Top: non-local means denoising of an image
 	with a fine-grained texture, acquired by \emph{in situ}
@@
 	tomography} \citep{Bouttes2015}.
-	\textbf{Feature extraction -} Top: Hubble deep field (NASA,
+	\textbf{b) Feature extraction -} Top: Hubble deep field (NASA,
 	public domain), blob detection using the
@@
 	leading eigenvalue of the Hessian matrix.
-	\textbf{Segmentation - } Top: super-pixel segmentation
+	\textbf{c) Segmentation - } Top: super-pixel segmentation
 	of a CT slice of the human head \citep{tomo_wikipedia}, using
@@
 	histogram-determined markers (bottom-left corner).
-	\textbf{Measures -} Top: visualization of local diameter
+	\textbf{d) Measures -} Top: visualization of local diameter
 	(color-coded on the skeleton curve) of an
@@
 Getreuer2012} is ideal for restoring piecewise-constant images (see
-Fig.~\ref{fig:tomo_gallery}), such as images with a small number of
+Fig.~\ref{fig:tomo_gallery} a)), such as images with a small number of
 phases encountered in materials science \citep{Bouttes2015}. Conversely,
 images with a fine-grained texture are better preserved with non-local
-means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery}).
+means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery} a)).
 
@@
 \citep{Ashiotis2015}, such as the Laplacian of Gaussian method (see
-Fig.~\ref{fig:tomo_gallery}). In order to detect thin boundaries, the
+Fig.~\ref{fig:tomo_gallery} b)). In order to detect thin boundaries, the
 ridges of an image can be identified as regions for which the leading eigenvalue
-of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery}).
+of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery} b)).
 
@@
 close together both in color- and spatial distance (see
-Fig.~\ref{fig:tomo_gallery}). Region-growing algorithms, such as the
+Fig.~\ref{fig:tomo_gallery} c)). Region-growing algorithms, such as the
 morphological watershed or the random walker \citep{Grady2006}, propagate
 the labels of user-defined markers through the image (see
-Fig.~\ref{fig:tomo_gallery}). The active contour algorithm
+Fig.~\ref{fig:tomo_gallery} c)). The active contour algorithm
 \citep{Kass1988} fits snake contours to features of the image, such as
@@
 size, extent, center of mass or mean intensity value are accessed with
-\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery}). Local
+\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery} d)). Local
 characteristics of a region can be retrieved as well:
-Fig.~\ref{fig:tomo_gallery} shows how the local diameter of open
+Fig.~\ref{fig:tomo_gallery} d) shows how the local diameter of open
 porosity is measured by combining a skeletonization of the porosity

### 2016-08-21 skimage_tomo.tex
Added mayavi example

@@
 
+\begin{figure*}[ht!]
+    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
+    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
+             plot and text output (middle), and free-form narrative text (bottom).
+             This makes it ideal to record and report code-based analyses.
+             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
+ \label{fig:jupyter}}
+\end{figure*}
+
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
@@
 tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
-
-\begin{figure*}
-    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
-    \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
-             plot and text output (middle), and free-form narrative text (bottom).
-             This makes it ideal to record and report code-based analyses.
-             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
- \label{fig:jupyter}}
-\end{figure*}
 
@@
 \texttt{mayavi} is based on the VTK toolkit. It exposes a simple API for
-visualizing data passed as \texttt{numpy} arrays. For more advanced
-visualizations, a large majority of VTK capabilities can be accessed
-through mayavi's pipeline API.
-\texttt{mayavi} offers a good trade-off between simplicity of use for
-common operations, and accessibility to more sophisticated
-capabilities such as responsive
+visualizing data passed as \texttt{numpy} arrays. For example,
+visualizing the surface of binary data can be written as
+\begin{lstlisting}[language=Python]
+# synthetic binary array from skimage.data
+im = data.binary_blobs(length=400, n_dim=3).astype(np.uint8)
+# visualization
+from mayavi import mlab
+mlab.contour3d(im)
+mlab.outline()
+\end{lstlisting}
+(see Fig.~\ref{fig:mayavi} for the resulting visualization).
+
+For more advanced visualizations, a large majority of VTK capabilities
+can be accessed through mayavi's pipeline API. \texttt{mayavi} offers a
+good trade-off between simplicity of use for common operations, and
+accessibility to more sophisticated capabilities such as responsive
 visualizations.
+
+\begin{figure}[ht]
+    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
+    \caption{Simple visualization realized with Mayavi.
+ \label{fig:mayavi}}
+\end{figure}
 

### 2016-08-21 skimage_tomo.tex
Sections Getting started and Limitations

@@
 2-D and 3-D images, thanks to its intuitive menus and graphical tools,
-and the wealth of plugins contributed by a vivid
-community \citep{Schindelin2015}. For 3-D images, commercial tools such
-as Avizo 3D software (TM) are appreciated for an intuitive graphical
-pipeline and advanced 3D visualization. Alternatively, the use of a
-programming language gives finer control and more possibilities, provided
-classical processing algorithms can be called from libraries -- thereby
-limiting the complexity of the programming task and the risk of bugs. Matlab (TM) and its
-image processing toolbox are popular in the academic community of
-computer vision and image processing. The Python language is widely used
-in the scientific world and in synchrotron facilities. As a
-general-purpose language, Python is used in synchrotrons to control
-device servers \citep{pytango}, to access raw data of X-ray
-detectors \citep{Knudsen2013}, to reconstruct tomography volumes from
-radiographs \citep{Gursoy2014, Mirone2014}, and in data
-processing packages for macromolecular cristallography \citep{Adams2010},
-azimuthal integration of diffraction data \citep{Ashiotis2015}, or
-fluorescence analysis \citep{pymca}.
+and the wealth of plugins contributed by a vivid community
+\citep{Schindelin2015}. For 3-D images, commercial tools such as Avizo 3D
+software (TM) are appreciated for an intuitive graphical pipeline and
+advanced 3D visualization. Alternatively, the use of a programming
+language gives finer control, a better reproducibility and more
+possibilities, provided classical processing algorithms can be called
+from libraries -- thereby limiting the complexity of the programming task
+and the risk of bugs. Matlab (TM) and its image processing toolbox are
+popular in the academic community of computer vision and image
+processing. The Python language is widely used in the scientific world
+and in synchrotron facilities. As a general-purpose language, Python is
+used in synchrotrons to control device servers \citep{pytango}, to access
+raw data of X-ray detectors \citep{Knudsen2013}, to reconstruct
+tomography volumes from radiographs \citep{Gursoy2014, Mirone2014}, and
+in data processing packages for macromolecular cristallography
+\citep{Adams2010}, azimuthal integration of diffraction data
+\citep{Ashiotis2015}, or fluorescence analysis \citep{pymca}.
 
@@
 \lstinputlisting[language=Python]{io_coll.py}
-Raw data formats can be opened using the \texttt{NumPy} functions \texttt{fromfile} or \texttt{memmap}, and \texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
+Raw data formats can be opened using the \texttt{NumPy} functions
+\texttt{fromfile} (to load the array into memory) or \texttt{memmap} (to
+keep the array on disk). The following code creates an array from a
+raw image file of unsigned 16-bit integers with a header of 1024 bytes 
+\begin{lstlisting}
+im = np.memmap('image.edf', shape=(2048, 2048), offset=1024, dtype=np.uint16)
+\end{lstlisting}
+For every raw data specification, it is thus very easy to write a reader
+using \texttt{np.memmap} (see for example
+\url{https://github.com/jni/python-redshirt}). 
+\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
+\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
 
@@
 The Jupyter notebook \citep{Kluyver2016} is a web application that grew
-out of the IPython project. Jupyter notebooks provide an interactive development
-environment within a web browser, where live code can be enriched
-by explanatory text, equations and visualizations (Fig.~\ref{fig:jupyter}).
-As of July 2016, more than 500,000 Jupyter notebooks were posted on GitHub,
-demonstrating their wide adoption by the community as workflow-sharing
-tools (\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
+out of the IPython project. Jupyter notebooks provide an interactive
+development environment within a web browser, where live code can be
+enriched by explanatory text, equations and visualizations
+(Fig.~\ref{fig:jupyter}). Jupyter notebooks render directly as webpages
+on GitHub, making them a straightforward tool to publish online a
+script and its output. As of July 2016, more than 500,000 Jupyter
+notebooks were posted on GitHub, demonstrating their wide adoption by the
+community as workflow-sharing tools
+(\url{http://archive.ipython.org/media/SciPy2016JupyterLab.pdf}).
 
@@
 
+\paragraph{Capabilities.}
+
 \texttt{scikit-image} offers most classical image processing operations,
@@
 Given the large size of tomography datasets, the execution speed of image
-processing operations is of critical concern. \texttt{scikit-image} relies mostly
-on calls to \texttt{NumPy} operations, of which most are performed in
-optimized compiled code (C or Fortran). Performance-critical parts of \texttt{scikit-image}
-that cannot call efficient \texttt{NumPy} code are implemented in
-\texttt{Cython}. \texttt{Cython} \citep{Behnel2011} is an extension of the
-Python language that supports explicit type declarations, and is compiled
-directly to C.
+processing operations is of critical concern. \texttt{scikit-image}
+relies mostly on calls to \texttt{NumPy} operations, of which most are
+performed in optimized compiled code (C or Fortran). Performance-critical
+parts of \texttt{scikit-image} that cannot call efficient \texttt{NumPy}
+code are implemented in \texttt{Cython}. \texttt{Cython}
+\citep{Behnel2011} is an extension of the Python language that supports
+explicit type declarations, and is compiled directly to C. Therefore, the
+performance of \texttt{scikit-image} can be close to the one of libraries
+written in a compiled language such as C++ or Java. For example,
+computing the watershed segmentation of a 2000x2000 array of floats into
+1000 regions took about 1 s using 1 CPU of an off-the-shelf laptop, and
+10 s for a 256x256x256 image segmented into 2000 regions. Similar
+timescales were obtained with \texttt{mahotas}, a Python package
+implemented exclusively in C++ \citep{Coelho2013} (with a slight advantage
+for \texttt{mahotas}).
 
@@
 (512, 512)
->>> # chunks of size 120 with 8-pixel overlap
->>> chunks = util.view_as_windows(im, (128, 128), step=120)
+>>> # chunks of size 134 with 8-pixel overlap
+>>> chunks = util.view_as_windows(im, (134, 134), step=126)
 >>> chunks.shape
-(4, 4, 128, 128)
+(4, 4, 134, 134)
 \end{lstlisting}
@@
 
-\section*{Documentation and getting help}
+\section*{Documentation}
 
@@
 ensures that new features are propagated to users on a regular basis.
+
+\section*{Current limitations and challenges}
+
+While have insisted on the assets of \texttt{scikit-image} for processing
+X-ray images, one should be aware of current limitations of the package.
+
+\paragraph{Speed of execution.} Although \texttt{scikit-image} approaches
+the speed of execution of compiled (C++, Java) code, it cannot reach the
+performance of code optimized for the GPU. \texttt{scikit-image} is not
+the best tool for ultrafast computations where the workflow is known
+beforehand, simple and stable. However, it is an excellent tool for
+exploring image data interactively and testing different algorithms -- an
+important component of data processing in scientific work --, and its
+speed of execution is good enough to process the Gb-sized tomographic
+images in seconds to minutes.
+
+\paragraph{3-D compatibility.} At the moment, about two thirds of
+\texttt{scikit-image} functions take indifferently 2D or 3D arrays. It is
+planned to increase this compatibility in the future.
+
+\paragraph{Documentation for domain-specific applications.} Some image
+processing libraries or applications address a specific scientific
+domains, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
+biological images. The documentation of such projects often showcases
+examples that are close to the experience of the targeted community.
+Since \texttt{scikit-image} is application-agnostic,
+applications such as tomographic imaging are not mentioned in detail in the
+documentation of \texttt{scikit-image}. A possible improvement would be
+to write comprehensive tutorials addressing specific communities, and to
+reference these tutorials from the main \texttt{scikit-image}
+documentation.
+
+\section*{Getting started}
+
+Scientists interested in experimenting with \texttt{scikit-image} are
+invited to read the installation instructions on
+\url{http://scikit-image.org/docs/stable/install.html}.
+\texttt{scikit-image} can be installed either bundled in a Scientific
+Python distribution, such as Anaconda or Canopy, or alone (with its
+dependencies) using a installer/packager program such as pip or Ubuntu's
+Synaptic.
+
+The Getting started section of the online User Guide
+(\url{http://scikit-image.org/docs/dev/user_guide/getting_started.html})
+is a good starting point, as well as the other sections of the user
+guide. Examples of the gallery
+(\url{http://scikit-image.org/docs/dev/auto_examples/}) can be used to
+find applications close to one's needs. Although most examples of the
+gallery use 2D images, most functions can be used with 3D images as well.
+
+Assistance on matters not covered by the documentation is provided to
+users either on the dedicated mailing-list
+\url{scikit-image@googlegroups.com} or on StackOverflow
+\url{http://stackexchange.com/filters/87964/scikit-image}.
 

### 2016-08-21 skimage_tomo.tex
Minor edits

@@
 \begin{figure*}
-    \centerline{\includegraphics[width=0.8\textwidth]{ecosystem_landscape}}
+    \centerline{\includegraphics[width=0.77\textwidth]{ecosystem_landscape}}
     \caption{\csentence{\texttt{scikit-image} and the Scientific Python
@@
 \texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
-\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
+%\texttt{hdf5} files are accessed using modules such as \texttt{h5py}, \texttt{pytables}.
 
@@
 
-\begin{figure*}
+\begin{figure*}[ht!]
     \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
@@
 \begin{figure*}[ht!]
-    \centerline{\includegraphics[width=0.8\textwidth]{jupyter_example}}
+    \centerline{\includegraphics[width=0.75\textwidth]{jupyter_example}}
     \caption{\csentence{The Jupyter notebook} allows mixing of computer code (top),
@@
 
-\begin{figure}[ht]
+\begin{figure}[ht!]
     \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
@@
 the speed of execution of compiled (C++, Java) code, it cannot reach the
-performance of code optimized for the GPU. \texttt{scikit-image} is not
-the best tool for ultrafast computations where the workflow is known
-beforehand, simple and stable. However, it is an excellent tool for
-exploring image data interactively and testing different algorithms -- an
-important component of data processing in scientific work --, and its
-speed of execution is good enough to process the Gb-sized tomographic
-images in seconds to minutes.
+performance of code optimized for the GPU. At the moment,
+\texttt{scikit-image} is not the best tool for ultrafast computations
+where the workflow is known beforehand, simple and stable. However, it is
+an excellent tool for exploring image data interactively and testing
+different algorithms -- an important component of data processing in
+scientific work --, and its speed of execution is good enough to process
+the gigabyte-sized tomographic images in seconds to minutes. Moreover,
+multiprocessing capabilities of \texttt{scikit-image} should improve in
+the future.
 

### 2016-08-22 skimage_tomo.tex
Edit for limitations section

@@
 scientific work --, and its speed of execution is good enough to process
-the gigabyte-sized tomographic images in seconds to minutes. Moreover,
-multiprocessing capabilities of \texttt{scikit-image} should improve in
-the future.
+gigabyte-sized tomographic images in seconds to minutes. Moreover,
+the multiprocessing capability of \texttt{scikit-image} should improve in
+the near future.
 
 \paragraph{3-D compatibility.} At the moment, about two thirds of
-\texttt{scikit-image} functions take indifferently 2D or 3D arrays. It is
-planned to increase this compatibility in the future.
+\texttt{scikit-image} functions transparently handle 2D or 3D arrays, with
+the remainder limited to 2D analysis, often unnecessarily. Improved support
+for 3D and higher-dimensional volumes is in the project roadmap, however.
 

### 2016-08-22 skimage_tomo.tex
Minor edits

@@
     \texttt{scikit-image} combines a gentle learning curve, versatile
-    image processing capabilities, and the scalable performances required
+    image processing capabilities, and the scalable performance required
     for the high-throughput analysis of X-ray imaging data.
@@
 advanced 3D visualization. Alternatively, the use of a programming
-language gives finer control, a better reproducibility and more
+language gives finer control, better reproducibility, and more complex analysis
 possibilities, provided classical processing algorithms can be called

### 2016-08-22 skimage_tomo.tex
Wait for end of proposition to cite

@@
 seconds \citep{Maire2014}. New modalities such as single-bunch
-imaging \citep{Rack2014} provide a time resolution down to the nanosecond
-for radiography. However, the time subsequently spent in processing the
+imaging provide a time resolution down to the nanosecond
+for radiography \citep{Rack2014}. However, the time subsequently spent in processing the
 images has not decreased as much, so that the outcome of a successful
@@
 processing packages. \texttt{scikit-image} has seen tremendous growth
-since its creation in 2009, both in terms of users and proposed features.
+since its creation in 2009, both in terms of users and included features.
 In addition to the growing number of scientific teams that use

### 2016-08-22 skimage_tomo.tex
Version submitted

@@
 (API), based almost exclusively on
-functions. Most functions take an image (\emph{i.e} a multi-dimensional
+functions. Most functions take an image (\emph{i.e.} a multi-dimensional
 array) as input parameter:
@@
 
-The \texttt{scikit-image} paper of 2014 has been cited by 120 research
-works (as of August 2016, according to Google Scholar), among which
-studies that used X-ray imaging in fields such as medical imaging
-\citep{Shen2015, Malan2016, Blackledge2016}, materials science
-\citep{Bouttes2015} or geoscience \citep{Schluter2014}.
+The \texttt{scikit-image} paper of 2014 \citep{Vanderwalt2014} has been
+cited by 120 research works (as of August 2016, according to Google
+Scholar), among which studies that used X-ray imaging in fields such as
+medical imaging \citep{Shen2015, Malan2016, Blackledge2016}, materials
+science \citep{Bouttes2015} or geoscience \citep{Schluter2014}.
 
@@
 
-While have insisted on the assets of \texttt{scikit-image} for processing
+While we have insisted on the assets of \texttt{scikit-image} for processing
 X-ray images, one should be aware of current limitations of the package.
@@
 processing libraries or applications address a specific scientific
-domains, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
+domain, such as CellProfiler \citep{Carpenter2006, Lamprecht2007} for
 biological images. The documentation of such projects often showcases

### 2016-08-25 skimage_tomo.tex
Add suggestions for deficiencies section

@@
 More than 170 individuals have contributed to the package. The large
-number of developers and users is a key element of the sustainability of
-\texttt{scikit-image}. The
+number of developers and users key to project's sustainability. The
 development process takes place on GitHub
@@
 
-While we have insisted on the assets of \texttt{scikit-image} for processing
-X-ray images, one should be aware of current limitations of the package.
+While we emphasize the assets of \texttt{scikit-image} for processing
+X-ray images, one should be aware of current limitations.
 
@@
 the speed of execution of compiled (C++, Java) code, it cannot reach the
-performance of code optimized for the GPU. At the moment,
+performance of code optimized for the GPU, or the hand-tuned
+CPU-specific optimizations found in OpenCV. At the moment,
 \texttt{scikit-image} is not the best tool for ultrafast computations
@@
 different algorithms -- an important component of data processing in
-scientific work --, and its speed of execution is good enough to process
+scientific work --, and its speed of execution is sufficient for processing
 gigabyte-sized tomographic images in seconds to minutes. Moreover,
-the multiprocessing capability of \texttt{scikit-image} should improve in
+the multiprocessing capability of \texttt{scikit-image} is likely to improve in
 the near future.
 
-\paragraph{3-D compatibility.} At the moment, about two thirds of
+\paragraph{3-D compatibility.} Currently, about two thirds of
 \texttt{scikit-image} functions transparently handle 2D or 3D arrays, with
 the remainder limited to 2D analysis, often unnecessarily. Improved support
-for 3D and higher-dimensional volumes is in the project roadmap, however.
+for 3D and higher-dimensional volumes is on the project roadmap.
 
@@
 to write comprehensive tutorials addressing specific communities, and to
-reference these tutorials from the main \texttt{scikit-image}
+refer to these tutorials from the main \texttt{scikit-image}
 documentation.
@@
 Scientists interested in experimenting with \texttt{scikit-image} are
-invited to read the installation instructions on
+invited to read the installation instructions at
 \url{http://scikit-image.org/docs/stable/install.html}.
 \texttt{scikit-image} can be installed either bundled in a Scientific
-Python distribution, such as Anaconda or Canopy, or alone (with its
-dependencies) using a installer/packager program such as pip or Ubuntu's
-Synaptic.
+Python distribution, such as Anaconda or Canopy, or stand alone (along with its
+dependencies) using an installer/packager such as pip or Ubuntu's
+Aptitude.
 
-The Getting started section of the online User Guide
+The Getting Started section of the online User Guide
 (\url{http://scikit-image.org/docs/dev/user_guide/getting_started.html})
-is a good starting point, as well as the other sections of the user
-guide. Examples of the gallery
-(\url{http://scikit-image.org/docs/dev/auto_examples/}) can be used to
-find applications close to one's needs. Although most examples of the
-gallery use 2D images, most functions can be used with 3D images as well.
+provides a good launch pad for beginners, and gently leads into other sections of the user
+guide. A gallery of examples
+(\url{http://scikit-image.org/docs/dev/auto_examples/}) lets users
+find applications close to their needs. Although most examples in the
+gallery use 2D images, many are applicable to 3D images as well.
 
-Assistance on matters not covered by the documentation is provided to
-users either on the dedicated mailing-list
-\url{scikit-image@googlegroups.com} or on StackOverflow
-\url{http://stackexchange.com/filters/87964/scikit-image}.
+Assistance on matters not covered by the documentation is provided on
+the dedicated mailing-list \url{scikit-image@googlegroups.com} or on
+StackOverflow
+\url{http://stackoverflow.com/questions/tagged/scikit-image}.
 

### 2016-10-24 process/ct_slic.py
Minor cleaning of code and use of MPL OO interface

@@ -1,16 +1,13 @@
-import numpy as np
 import matplotlib.pyplot as plt
 
 from skimage import io, segmentation
 
 im = io.imread('ct_wikipedia.jpg', as_grey=True)
-#pixels = segmentation.slic(im, n_segments=600, compactness=2.e-4)
 pixels = segmentation.felzenszwalb(im, scale=200)
 
-plt.figure(figsize=(5, 5))
-plt.imshow(segmentation.mark_boundaries(im, pixels))
-plt.axis('off')
-plt.tight_layout()
-plt.show()
+fig, ax = plt.subplots(figsize=(5, 5), tight_layout=True)
+ax.imshow(segmentation.mark_boundaries(im, pixels))
+ax.axis('off')
+fig.show()
 plt.savefig('super_pixels.png')
 

### 2016-10-24 process/denoising_demix2d.py

@@ -1,4 +1,3 @@
-import numpy as np
 from skimage import restoration, io
 import matplotlib.pyplot as plt
 

### 2016-10-24 process/denoising_nlm.py

@@ -1,4 +1,3 @@
-import numpy as np
 from skimage import restoration, io, img_as_float
 import matplotlib.pyplot as plt
 

### 2016-10-24 process/plot_random_walker_segmentation.py

@@ -21,7 +21,6 @@ values, and use the random walker for the segmentation.
 
 """
 import numpy as np
-import matplotlib.pyplot as plt
 
 from skimage.segmentation import random_walker
 from skimage.data import binary_blobs

### 2016-10-29 skimage_tomo.tex
Modified section titles to please the publisher
Replace gist citation with Zenodo GH repo
Minor changes following comments from reviewers.

@@
 
-\title{Analyzing X-ray images in Python with scikit-image}
+\title{Analyzing microtomography data with Python and the scikit-image
+library}
 
@@
    %noteref={n1},                        % id's of article notes, if any
-   email={emmanuelle.gouillart@saint-gobain.com}   % email address
+   email={emmanuelle.gouillart@nsup.org}   % email address
 ]{\fnm{Emmanuelle} \snm{Gouillart}}
@@
 users to process their images. ImageJ \citep{Abramoff2004, Schneider2012}
-and its distribution Fiji \citep{Schindelin2012} is a popular tool for
-2-D and 3-D images, thanks to its intuitive menus and graphical tools,
-and the wealth of plugins contributed by a vivid community
-\citep{Schindelin2015}. For 3-D images, commercial tools such as Avizo 3D
-software (TM) are appreciated for an intuitive graphical pipeline and
-advanced 3D visualization. Alternatively, the use of a programming
-language gives finer control, better reproducibility, and more complex analysis
-possibilities, provided classical processing algorithms can be called
-from libraries -- thereby limiting the complexity of the programming task
-and the risk of bugs. Matlab (TM) and its image processing toolbox are
-popular in the academic community of computer vision and image
-processing. The Python language is widely used in the scientific world
-and in synchrotron facilities. As a general-purpose language, Python is
-used in synchrotrons to control device servers \citep{pytango}, to access
-raw data of X-ray detectors \citep{Knudsen2013}, to reconstruct
-tomography volumes from radiographs \citep{Gursoy2014, Mirone2014}, and
-in data processing packages for macromolecular cristallography
-\citep{Adams2010}, azimuthal integration of diffraction data
-\citep{Ashiotis2015}, or fluorescence analysis \citep{pymca}.
+and its distribution Fiji \citep{Schindelin2012} is a popular
+general-purpose tool for 2-D and 3-D images, thanks to its intuitive
+menus and graphical tools, and the wealth of plugins contributed by a
+vivid community \citep{Schindelin2015}. Software specialized in analyzing
+synchrotron data are available as well, such as XRDUA~\citep{xrdua} for
+diffraction images obtained in powder diffraction analysis, or  For 3-D
+images, commercial tools such as Avizo 3D software (TM), or
+ToolIP/MaviKit~\citep{mavi} are appreciated
+for an intuitive graphical pipeline and advanced 3D visualization. Some
+synchrotrons have even developed their own tools for volume processing,
+such as Pore3D~\citep{Brun2010} at the Elettra facility. Alternatively,
+the use of a programming language gives finer control, better
+reproducibility, and more complex analysis possibilities, provided
+classical processing algorithms can be called from libraries -- thereby
+limiting the complexity of the programming task and the risk of bugs.
+Matlab (TM) and its image processing toolbox are popular in the academic
+community of computer vision and image processing. The Python language is
+widely used in the scientific world and in synchrotron facilities. As a
+general-purpose language, Python is used in synchrotrons to control
+device servers \citep{pytango, Sugandhi2016, nsls-ii}, to access raw data
+of X-ray detectors \citep{Knudsen2013}, to reconstruct tomography volumes
+from radiographs \citep{Gursoy2014, Mirone2014}, and in data processing
+packages for macromolecular cristallography \citep{Adams2010}, azimuthal
+integration of diffraction data \citep{Ashiotis2015}, or fluorescence
+analysis \citep{pymca, Sole2007}.
 
-\texttt{scikit-image} \citep{Vanderwalt2014} is a general-purpose image
-processing library for the Python language, and a component of the ecosystem of
-Python scientific modules commonly known as Scientific
-Python \citep{Oliphant2007}. Like the rest of the ecosystem,
-\texttt{scikit-image} is released under a permissive open-source license and is
-available free of charge. Most of \texttt{scikit-image} is compatible with both 2-D and
-3-D images, so that it can be used for a large number of imaging modalities,
-such as microscopy, radiography or tomography. In this article, we explain how
-\texttt{scikit-image} can be used for processing data acquired in X-ray
-imaging experiments, with a focus on microtomography 3-D images. This
-article does not intend to be a pedagogical tutorial on \texttt{scikit-image}
-for X-ray imaging, but rather to explain the rationale behind the package, and
-provide various examples of its capabilities.
+%\vskip 1cm 
+\texttt{scikit-image}
+\citep{Vanderwalt2014} is a general-purpose image processing library for
+the Python language, and a component of the ecosystem of Python
+scientific modules commonly known as Scientific Python
+\citep{Oliphant2007}. Like the rest of the ecosystem,
+\texttt{scikit-image} is released under a permissive open-source license
+and is available free of charge. Most of \texttt{scikit-image} is
+compatible with both 2-D and 3-D images, so that it can be used for a
+large number of imaging modalities, such as microscopy, radiography or
+tomography. In this article, we explain how \texttt{scikit-image} can be
+used for processing data acquired in X-ray imaging experiments, with a
+focus on microtomography 3-D images. This article does not intend to be a
+pedagogical tutorial on \texttt{scikit-image} for X-ray imaging, but
+rather to explain the rationale behind the package, and provide various
+examples of its capabilities.
 
-\section*{Overview and first steps}
+\section*{Methods -- Overview and first steps}
 
@@
 
-\begin{figure*}
+\begin{figure*}[!htb]
     \centerline{\includegraphics[width=0.77\textwidth]{ecosystem_landscape}}
@@
 
-\begin{figure*}[ht!]
+\begin{figure*}[!htb]
     \centerline{\includegraphics[width=0.99\textwidth]{spyder_process}}
@@
 
-\begin{figure*}[ht!]
+\begin{figure*}[!htb]
     \centerline{\includegraphics[width=0.75\textwidth]{jupyter_example}}
@@
 
-\begin{figure}[ht!]
-    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
-    \caption{Simple visualization realized with Mayavi.
- \label{fig:mayavi}}
-\end{figure}
-
 \paragraph{Advanced toolkits for signal processing and data science.}
@@
 \texttt{scikit-image}.
+
+\section*{Results}
+\begin{figure}[!htb]
+    \centerline{\includegraphics[width=0.6\columnwidth]{mayavi_example}}
+    \caption{\csentence{Simple 3-D visualization} realized with Mayavi.
+ \label{fig:mayavi}}
+\end{figure}
 
@@
 \texttt{scikit-image} offers most classical image processing operations,
-such as exposure and color adjustment, filtering,
-segmentation, feature extraction, geometric transformations, and
-measurements of region characteristics. In addition, some advanced
+such as exposure and color adjustment, filtering, segmentation, feature
+extraction, geometric transformations, and measurements of region
+characteristics. In addition to common operations, some advanced
 algorithms are also implemented, a selection of which is illustrated in
-Fig.~\ref{fig:tomo_gallery}.
+Fig.~\ref{fig:tomo_gallery}. In the following, we briefly illustrate how
+\texttt{scikit-image} can be used for some typical image processing
+tasks encountered when analyzing tomographic images: denoising, mid-range
+feature detection, segmentation and measurement of region properties. For
+the sake of brevity, other tasks such as contrast manipulation or
+geometric transformations are not described here; the interested reader
+is referred to the documentation of \texttt{scikit-image}.
 
 Tomographic images often suffer from artifacts or poor signal-to-noise
-ratio. Several denoising filters are available for restoring these
-images, ranging from general-purpose median and bilateral
-filters to those more suited to specific applications. For example, total-variation denoising \citep{Chambolle2004,
-Getreuer2012} is ideal for restoring piecewise-constant images (see
+ratio. Therefore, \emph{denoising} data is often the first step of an
+image processing workflow. Several denoising filters are available for
+restoring these images, ranging from general-purpose median and
+bilateral filters to those more suited to specific applications. For
+example, total-variation denoising \citep{Chambolle2004, Getreuer2012} is
+ideal for restoring piecewise-constant images (see
 Fig.~\ref{fig:tomo_gallery} a)), such as images with a small number of
@@
 images with a fine-grained texture are better preserved with non-local
-means denoising \citep{Buades2005} (see Fig.~\ref{fig:tomo_gallery} a)).
+means denoising, a patch-based algorithm \citep{Buades2005} (see
+Fig.~\ref{fig:tomo_gallery} a)).
 
-\texttt{scikit-image} offers a wide variety of functions for detecting
-geometrical features of interest in an image. Peaks in 2D
-diffraction images can be extracted using blob detection methods
-\citep{Ashiotis2015}, such as the Laplacian of Gaussian method (see
-Fig.~\ref{fig:tomo_gallery} b)). In order to detect thin boundaries, the
-ridges of an image can be identified as regions for which the leading eigenvalue
-of the local Hessian matrix is high (see Fig.~\ref{fig:tomo_gallery} b)).
+Detecting the presence of objects or extracting pixels corresponding to
+objects (a task known as segmentation) is an important task of image
+analysis for medical or materials science applications.
+\texttt{scikit-image} offers a wide variety of functions for
+\emph{detecting geometrical features} of interest in an image. In order
+to detect thin boundaries, the ridges of an image can be identified as
+regions for which the leading eigenvalue of the local Hessian matrix is
+high (see Fig.~\ref{fig:tomo_gallery} b)). In the Fourier space, peaks in
+2D Bragg diffraction patterns can be extracted using blob detection
+methods \citep{Ashiotis2015}, such as the Laplacian of Gaussian method
+(see Fig.~\ref{fig:tomo_gallery} b)).
 
-Segmentation of regions of interest can be achieved using one of various
+\emph{Segmentation} of regions of interest can be achieved using one of various
 strategies, depending on the characteristics of the image. Images with a
@@
 
-The characteristics of labeled regions (particles, porosities, organs,
-\dots) resulting from a segmentation can be measured using the
-\texttt{measure} submodule. The different connected components (e.g.
-bubbles or non-touching particles) of a binary image are labeled with the
-\texttt{measure.label} function. Properties of labeled regions such as
-size, extent, center of mass or mean intensity value are accessed with
-\texttt{measure.regionprops} (see Fig.~\ref{fig:tomo_gallery} d)). Local
-characteristics of a region can be retrieved as well:
-Fig.~\ref{fig:tomo_gallery} d) shows how the local diameter of open
-porosity is measured by combining a skeletonization of the porosity
-channels, and the distance transform to the other phase measured on the
-skeleton.
+Following segmentation, the characteristics of labeled regions
+(particles, porosities, organs, \dots) resulting from a segmentation can
+be measured using the \texttt{measure} submodule. The different connected
+components (e.g. bubbles or non-touching particles) of a binary image are
+labeled with the \texttt{measure.label} function. Properties of labeled
+regions such as size, extent, center of mass or mean intensity value are
+accessed with \texttt{measure.regionprops} (see
+Fig.~\ref{fig:tomo_gallery} d)). Local characteristics of a region can be
+retrieved as well: Fig.~\ref{fig:tomo_gallery} d) shows how the local
+diameter of open porosity is measured by combining a skeletonization of
+the porosity channels, and the distance transform to the other phase
+measured on the skeleton.
 
@@
 
-\section*{Current limitations and challenges}
+\section*{Discussion -- Current limitations and challenges}
 
@@
 performance of code optimized for the GPU, or the hand-tuned
-CPU-specific optimizations found in OpenCV. At the moment,
+CPU-specific optimizations found in OpenCV \citep{Pulli2012}. At the moment,
 \texttt{scikit-image} is not the best tool for ultrafast computations
@@
 
+\section*{Author's contributions}
+E. Gouillart, J. Nunez Iglesias and S. van der Walt conducted the
+research and wrote the paper. All authors read and approved the final
+manuscript.
+
 \section*{Acknowledgements}
@@
 
+\newpage
+~
+\newpage
+
+\section*{Figures}
+
+\listoffigures
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-31 answer_to_referees.txt
More modifications + answer to referres

Answer to Reviewer 1
====================

* Suggest also citing http://nsls-ii.github.io/ and                  
http://cars9.uchicago.edu/software/python/pyepics3/ along with pytango.

We have cited PyEPICS as well as NSLS-II.

* Figure 3 should use the mpl OO API instead of plt.  A gist does not
  seem like a sufficiently stable citation target.

plt is used in a lot of code examples for legacy reasons, but the OO API
of matplotlib is indeed preferable nowadays. We have modified Figure 3
accordingly. We generated a DOI with Zenodo for a more stable citation
target.

* The discussion about skimage functionality (fig 5) was very fast and
  felt a bit disjointed.

Image processing is a very broad field, and scikit-image provides a large
variety of processing operations. Therefore, we chose to illustrate only
a few capabilities of scikit-image, since a lengthy list would bore the
reader, while not being very instructive. Nevertheless, the choice of
these operations, and the link between them, might have been better
explained. We now explain why denoising, object detection and
measurements are important for processing microtomography images "In the
following, we briefly illustrate how scikit-image can be used for some
typical image processing tasks encountered when analyzing tomographic
images: denoising, mid-range feature detection, segmentation and
measurement of region properties. For the sake of brevity, other tasks
such as contrast manipulation or geometric transformations are not
described here; the interested reader is referred to the documentation
of scikit-image.", "Denoising data is often the first step of an image
processing workflow", "Detecting the presence of objects or extracting
pixels corresponding to objects (a task known as segmentation) is an
important task of image analysis for medical or materials science
applications.". We have also improved transitions between paragraphs.

* Given the recent discussions of system package managers vs conda/EPD vs
  pip (ex
http://www.curiousefficiency.org/posts/2016/09/python-packaging-ecosystem.html)
I suggest re-wording the getting started section.

Python packaging is a broad topic, that goes well beyond the scope of our
paper. As explained in the blog post cited by the referee, different
solutions each have their pros and cons. The purpose of the getting
started section is mostly to give some pointers to the readers, rather
than engaging in a discussion on packaging. For the sake of completeness,
we now mention conda as a command-line tool for Anaconda (the most common
use of conda).

Answer to Reviewer 2
====================

* The article "Analyzing X-ray images in Python with scikit-image"
describes a powerful open software package which is of high use to
analyze images. It is well written, of high importance for all people
dealing with heavy data-image processing. Hence, I can recommend
publication.

We thank the referee for his/her positive comments about our paper.

* the title is a bit misleading as it explicitly states "X-ray images"
  while the routines described are quite general, i.e.
would also work for MRI or confocal laser scanning data sets, indeed,
there is  no hard link to X-ray. Contrary, X-ray images
are a broader term then just the microtomographic data included in this
article: fluorescence mapping reveals X-ray images,
each pixel contains a spectrum (hyperspectral images) - something not to
be     considered with scikit but the mentioned PyMCA,
i.e. the latter is a dedicated X-ray software, the same for xrdua and
diffraction data / tomography. Especially as the journal
title contains "Chemical Imaging" this needs to be more clear considering
that  standard full-field X-ray imaging is a non-
analytical tool. The referee is not the most creative person in the
world, a    suggestion for a modification could look like that
"Analyzing image data in Python with scikit-image: the case of
microtomography" or similar

We understand the concern of the referee, and we have changed the title
to "Analyzing microtomography data with Python and the scikit-image
library".

- p. 1, l. 51 / right column: the list is a bit incomplete, as stated above,    
xrdua could be mentioned, also in terms of volume                               
image processing there is powerful commercial and non-commercial software we    
should be listed here as a matter of fairness so                                
the reader can make his own choice, i.e. AVS www.avs.com, pore3D from Elettra   
Synchrotrone, ToolIP

In addition to Aviso Fire, we now mention pore3D and ToolIP/Mavi. We also
mention XRDUA for processing powder diffraction images. To our knowledge,
AVS was more popular in the past that it is now in the tomography
community, therefore we preferred to cite the most popular software only.

- the Figures appear not ordered in the manuscript, i.e. Fig 1, Fig 4, Fig 2    
....

We apologize for this inconvenience, that is due to Latex optimizing
float placement. This should be corrected in the publisher's layout.

- p. 5, l. 47, left: "diffraction images" - define what precisely is considered,
i.e. Bragg diffraction images?

We now say "peaks in 2D Bragg diffraction patterns".

- Fig 3 and Fig 6 the font size in the images itself are on the limit,
  make sure they can still be read in the final article

We increased the font size in Figures 3 and 6 (modifying the layout of
Figure 6 to this end).

- Fig 5: for the non-synthetic data sets: could one perhaps state where the data
was taken, i.e. in the acknowledgement? Scale                                   
bars are also missing.

Scale bars were actually omitted on purpose, since Fig. 5 is a very busy
figure, and its interest lies mostly in the application of image
processing operations, not in the original samples and images
themselves.

We have acknowledged the origin of the membrane image of Fig. 5 (b),
which was the only non-synthetic image for which the origin was missing.

- p. 6, l. 47 and later: for example for the Watershed it is not only           
interesting to know the raw CPU consumption, also the                           
memory consumption is important: at least in the early days a watershed would   
need 16x[image size] as amount of memory to                                     
process which was often more limiting than the CPU time, same for the euclidean 
distance transformation

The watershed algorithm implemented in scikit-image (from Soille,
"Automated Basin Delineation from Digital Elevation Models Using
Mathematical Morphology", Signal Processing 20 (1990) 171-182.) is much
more memory-savvy, since it uses of the order of 5x as much memory as the
original image size. Indeed, the algorithm does not need a lot of
additional variables of the same size of the original image.

Although scikit-image is not designed specifically for images of the size
of tomography volumes, memory consumption is often improved and optimized
during the code review process. We now write: "During the code review
process, a close watch is also kept on memory consumption, since for
large image sizes, transfers between computer memory (RAM) and CPU cache
are often a serious performance bottleneck."

- Ref Armando Sole: perhaps consider also citing the corresponding paper        
V.A. Solé, E. Papillon, M. Cotte, Ph. Walter, J. Susini, A multiplatform code   
for the analysis of energy-dispersive X-ray fluorescence spectra, Spectrochim.  
Acta Part B 62 (2007) 63-68.

We are now citing this paper by Solé et al.

### 2016-10-31 skimage_tomo.tex
More modifications + answer to referres

@@
              This makes it ideal to record and report code-based analyses.
-             Screenshot from \url{https://gist.github.com/jni/3339985a016572f178d3c2f18e27ec0d}.
+             Screenshot from \cite{NunezIglesias2016}.
  \label{fig:jupyter}}
@@
 	Laplacian of Gaussian method. Bottom: ridge detection using the
-	leading eigenvalue of the Hessian matrix.
+	leading eigenvalue of the Hessian matrix, neuron image from
+	CREMI challenge (\url{https://cremi.org/data/}).
 	\textbf{c) Segmentation - } Top: super-pixel segmentation
@@
 The large size of the \texttt{scikit-image} community makes it likely for
-algorithmic improvements to be discussed regularly.
+algorithmic improvements to be discussed regularly. During the code review
+process, a close watch is also kept on memory consumption, since for
+large image sizes, transfers between computer memory (RAM) and CPU cache
+are often a serious performance bottleneck.
 
@@
 \begin{figure*}
-    \centerline{\includegraphics[width=0.99\textwidth]{figure_gallery}}
+    \centerline{\includegraphics[width=0.95\textwidth]{figure_gallery}}
 \caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
@@
 \texttt{scikit-image} can be installed either bundled in a Scientific
-Python distribution, such as Anaconda or Canopy, or stand alone (along with its
-dependencies) using an installer/packager such as pip or Ubuntu's
-Aptitude.
+Python distribution, such as Anaconda (conda command line) or Canopy, or
+stand alone (along with its dependencies) using a installer/packager such
+as pip or Ubuntu's Aptitude.
 
@@
   careful reading of the paper and useful suggestions. E. Gouillart
-  acknowledges the support of ANR project EDDAM ANR-11-BS09-027.
+  acknowledges the support of ANR project EDDAM ANR-11-BS09-027. CREMI
+  (https://cremi.org/data/) is acknowledged for the membrane image of
+  Fig.~\ref{fig:tomo_gallery} (b).
 

### 2016-11-01 answer_to_referees.txt
Final minor modifications before resubmission.

@@
 paper. As explained in the blog post cited by the referee, different
-solutions each have their pros and cons. The purpose of the getting
-started section is mostly to give some pointers to the readers, rather
+solutions each have their pros and cons. The purpose of the "getting
+started" section is mostly to give some pointers to the readers, rather
 than engaging in a discussion on packaging. For the sake of completeness,
@@
 
-We have acknowledged the origin of the membrane image of Fig. 5 (b),
+We have acknowledged the origin of the neurons image of Fig. 5 (b),
 which was the only non-synthetic image for which the origin was missing.

### 2016-11-01 skimage_tomo.tex
Final minor modifications before resubmission.

@@
 images, commercial tools such as Avizo 3D software (TM), or
-ToolIP/MaviKit~\citep{mavi} are appreciated
+ToolIP/MAVIkit~\citep{mavi} are appreciated
 for an intuitive graphical pipeline and advanced 3D visualization. Some
@@
 In this section, we provide a short overview of the typical use patterns of
-\texttt{scikit-image}, illutrated by short snippets of code. Since
+\texttt{scikit-image}, illustrated by short snippets of code. Since
 Python is a programming language, the user interacts with data objects and
@@
 \caption{\csentence{Gallery of examples of \texttt{scikit-image}.}
- The gallery of examples consists of an array of thumbnails (left), which link to example webpages, each centerered on a specific image processing task.
+ The gallery of examples consists of an array of thumbnails (left), which link to example webpages, each centered on a specific image processing task.
 Each webpage includes Python code generating a figure, the figure itself, and a short tutorial explaining the image processing operations and the code.
